---
title: "deer_burn"
author: "R Pienaar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 5, fig.height = 4)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```


Libraries

```{r}
# Load in libraries
library(camtrapR)
library(dplyr)
library(ggplot2)
library(devtools)
library(unmarked)
library(scales)
library(lubridate)
# Install autoOcc incase you have not yet
# devtools::install_github(
#   "mfidino/autoOcc",
#   build_vignettes = TRUE
# )
library(autoOcc)
library(extrafont)
citation("autoOcc")



```


```{r}

#Load deer tables
ct <- read.csv("C:/Users/ryanp/Documents/Dissertation/Chapter4_Camera traps/Camelot Exports/Record Tables/ct_summary.csv")
head(ct)

data <- read.csv("C:/Users/ryanp/Documents/Dissertation/Chapter4_Camera traps/Camelot Exports/Record Tables/Record_table_mainpulated.csv")
head(data)

# Create a detection history for each Year
camop <- cameraOperation(CTtable      = ct,
                                    stationCol   = "Station",
                                    sessionCol = "Session",
                                    setupCol     = "Setup_date",
                                    retrievalCol = "Retrieval_date",
                                    hasProblems  = FALSE,
                                    dateFormat   = "mdy")
# without trapping effort
DetHist1 <- detectionHistory(recordTable         = data,
                            camOp                = camop,
                           species = "Odocoileus hemionus",
                            stationCol = "Station",
                            speciesCol = "Species",
                            recordDateTimeCol = "Date",
                            recordDateTimeFormat = "mdy",
                            occasionLength = 14,
                            scaleEffort = FALSE,
                            timeZone = "MST",
                            day1 = "survey",
                            unmarkedMultFrameInput = TRUE)
DetHist1$detection_history

deerdh <- DetHist1$detection_history
head(deerdh)
s1 <- deerdh[,1:25]
#s1$Year <- 1
s2 <- deerdh[,26:50]
#s2$Year <- 2
s3 <- deerdh[,51:75]
#s3$Year <- 3
s4 <- deerdh[,76:100]
#s4$Year <- 4

dh <- rbind(s1,s2,s3,s4)

sequence <- rep(1:4, each = 32)
dh <- as.data.frame(dh)
dh$Year<- sequence
dh$site <- substr(row.names(dh),1,9)

#Create covariates for each site
deer_covariates <- as.data.frame(rownames(DetHist1$detection_history))
deer_covariates$Forest <- substr(deer_covariates$`rownames(DetHist1$detection_history)`,5,5)
deer_covariates$Fire <- substr(deer_covariates$`rownames(DetHist1$detection_history)`,7,7)
dh$Year

#### Create a list of seasons ####
# Create the original list of dates
start_date <- as.Date("2019-09-23")
original_dates <- seq.Date(start_date, by = "14 days", length.out = 100)
original_dates
# Function to determine the season
get_season <- function(date) {
  month <- month(date)
  if (month %in% c(11, 12, 1, 2)) {
    return("Winter")
  } else if (month %in% c(3, 4)) {
    return("Spring")
  } else if (month %in% c(5, 6, 7, 8)) {
    return("Summer")
  } else if (month %in% c(9, 10)) {
    return("Fall")
  }
}

# Create the new list of seasons
seasons <- sapply(original_dates, get_season)

# Print the list of seasons
seasons

########

colnames(deer_covariates) <- c("Site", "Forest", "Fire")

# examine data
head(dh)

#Create a Year column in DH

length(rownames(dh))

#### SPecies Summaries ####
speciessum<-  as.data.frame(table(data$Species))
table(data$Station,data$Species)

```

```{r}


##Deer
deer_y <- format_y(
  x = dh,
  site_column = "site",
  time_column = "Year",
  history_columns = 1:25
)



```

Determine best detection model to be used to answer all questions

```{r}

# make named list (don't worry about the warning)
Year_frame <- list(
   Year = matrix(
     dh$Year,
     ncol = dim(deer_y)[2],
     nrow = dim(deer_y)[1]
   ),
   Forest = deer_covariates$Forest,
   Fire = deer_covariates$Fire,
   Season = matrix(seasons,
                   ncol = dim(deer_y)[2],
     nrow = dim(deer_y)[1])
                   
 )


# modeling with no covariates
pnull <- auto_occ(
  formula = ~1  # detection
            ~1, # occupancy
  y = deer_y
)


p1 <- auto_occ(
      ~ Forest
      ~1,
      y= deer_y,
      det_covs = Year_frame
)

p2 <- auto_occ(
      ~ Fire
      ~1,
      y= deer_y,
      det_covs = Year_frame
)

p3 <- auto_occ(
      ~ Year
      ~1,
      y= deer_y,
      det_covs = Year_frame
)


p4 <- auto_occ(
      ~ Forest + Fire
      ~1,
      y= deer_y,
      det_covs = Year_frame
)

p5 <- auto_occ(
      ~ Forest * Fire
      ~1,
      y= deer_y,
      det_covs = Year_frame
)

p6 <- auto_occ(
      ~ Forest + Year
      ~1,
      y= deer_y,
      det_covs = Year_frame
)

p7 <- auto_occ(
      ~ Forest * Year
      ~1,
      y= deer_y,
      det_covs = Year_frame
)

p8 <- auto_occ(
      ~ Fire + Year
      ~1,
      y= deer_y,
      det_covs = Year_frame
)


p9 <- auto_occ(
      ~ Fire * Year
      ~1,
      y= deer_y,
      det_covs = Year_frame
)





detection.aic <- compare_models(
  list(null = pnull,
       Forest = p1,
       Fire = p2,
       Year = p3,
       `Forest+Fire` = p4,
       `Forest*Fire` = p5,
       `Forest+Year` = p6,
       `Forest*Year` =p7,
       `Fire+Year` = p8,
       `Fire*Year` = p9),
  digits = 2
)

dfd.table <- detection.aic
dfd.table
write.csv(dfd.table,"Deer_Fire_Detection.csv")
### Best model is model 7 Forest * Year acounting for 97% of the weight

```


Question 1
How does occupancy change in response to fire across forest types?

```{r}

q1 <- auto_occ(
  ~Forest * Year
  ~ Forest * Fire,
  y = deer_y,
  det_covs = Year_frame,
  occ_covs = Year_frame
)


summary(q1)



nd1 <- data.frame(Forest= "A", Fire=as.factor(1))
nd2 <- data.frame(Forest= "A", Fire=as.factor(0))
nd3 <- data.frame(Forest= "J", Fire=as.factor(1))
nd4 <- data.frame(Forest= "J", Fire=as.factor(0))
nd5 <- data.frame(Forest= "M", Fire=as.factor(1))
nd6 <- data.frame(Forest= "M", Fire=as.factor(0))

nd <- rbind(nd1,nd2,nd3,nd4,nd5,nd6)
nd

q1.predict <- predict(q1, type = "psi", newdata = nd, se.fit= TRUE)
q1.predict <- cbind(nd, q1.predict)
q1.predict

q1_b <- summary(q1)

dq1_b <- q1_b@rho
oq1_b <- q1_b@psi

write.csv(dq1_b, "Det_Deer_Q1_Betas.csv")
write.csv(oq1_b, "Occ_Deer_Q1_Betas.csv")

predict(q1, type = "psi", level=0.6)
predict(q1, type = "psi")

# Create the plot using the defined jitter position
ggplot(data = q1.predict, aes(x = factor(Forest, level = c("A", "M", "J")), y = estimate, 
                              colour = factor(Fire, level =c("0", "1")))) +
  geom_point(size = 2, position = position_dodge(0.5)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, position = position_dodge(0.5)) +
  ylab("Deer Occupancy")+
  theme_classic()+
  theme(text = element_text(family = "serif", size = 12))+
  scale_x_discrete(label = c("Aspen\nConifer","Oak\nMaple" ,
                             "Pinyon\nJuniper"
                             ))+
  scale_color_manual(values = c("0" = "blue", "1" = "red"),labels = c("Unburned", "Burned"))+
  theme(
    text = element_text(family = "serif", size = 12, color = "black"),
    axis.title = element_text(size = 12, color = "black"),
    axis.text = element_text(size = 12, color = "black"),
    legend.text = element_text(size = 12, color = "black"),
    legend.title = element_text(size = 12, color = "black"),
    plot.title = element_text(size = 12, color = "black"),
    plot.subtitle = element_text(size = 12, color = "black"),
    plot.caption = element_text(size = 12, color = "black")
  )+
  ylim(0,1)+
  xlab(element_blank())+
  labs(color = "Burn status")

#rerun without legend

ggplot(data = q1.predict, aes(x = factor(Forest, level = c("A", "M", "J")), y = estimate, 
                              colour = factor(Fire, level =c("0", "1")))) +
  geom_point(size = 2, position = position_dodge(0.5)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, position = position_dodge(0.5)) +
  ylab("Deer Occupancy")+
  theme_classic()+
  theme(text = element_text(family = "serif", size = 12))+
  scale_x_discrete(label = c("Aspen\nConifer","Oak\nMaple" ,
                             "Pinyon\nJuniper"
                             ))+
  scale_color_manual(values = c("0" = "blue", "1" = "red"),labels = c("Unburned", "Burned"))+
  theme(
    text = element_text(family = "serif", size = 12, color = "black"),
    axis.title = element_text(size = 12, color = "black"),
    axis.text = element_text(size = 12, color = "black"),
    legend.text = element_text(size = 12, color = "black"),
    legend.title = element_text(size = 12, color = "black"),
    plot.title = element_text(size = 12, color = "black"),
    plot.subtitle = element_text(size = 12, color = "black"),
    plot.caption = element_text(size = 12, color = "black")
  )+
  ylim(0,1)+
  xlab(element_blank())+
  labs(color = "Burn status")+
  theme(legend.position="none")

```

Question 2
How does occupancy change in response to fire severity across forest types?


```{r}

#Create covariates for each site


sev.df <- read.csv("C:/Users/ryanp/Documents/Dissertation/Chapter4_Camera traps/Dynamic_Occ/Chapter-4/FireSeverity.csv")
sev.df <-sev.df[-c(27,28),]

sev.df <- sev.df %>% replace(is.na(.), 0)

deer_covariates$FireSev <- sev.df$Fire_severity
head(deer_covariates)

```

Best detection for Fire Severity

```{r}


# make named list (don't worry about the warning)
Year_frame <- list(
   Year = matrix(
     dh$Year,
     ncol = dim(deer_y)[2],
     nrow = dim(deer_y)[1]
   ),
   Forest = deer_covariates$Forest,
   FireSev = deer_covariates$FireSev,
   Season = matrix(seasons,
                   ncol = dim(deer_y)[2],
     nrow = dim(deer_y)[1])
 )

# modeling with no covariates
pnull <- auto_occ(
  formula = ~1  # detection
            ~1, # occupancy
  y = deer_y
)



p1 <- auto_occ(
      ~ Forest
      ~1,
      y= deer_y,
      det_covs = Year_frame
)

p2 <- auto_occ(
      ~ FireSev
      ~1,
      y= deer_y,
      det_covs = Year_frame
)

p3 <- auto_occ(
      ~ Year
      ~1,
      y= deer_y,
      det_covs = Year_frame
)


p4 <- auto_occ(
      ~ Forest + FireSev
      ~1,
      y= deer_y,
      det_covs = Year_frame
)

p5 <- auto_occ(
      ~ Forest * FireSev
      ~1,
      y= deer_y,
      det_covs = Year_frame
)

p6 <- auto_occ(
      ~ Forest + Year
      ~1,
      y= deer_y,
      det_covs = Year_frame
)

p7 <- auto_occ(
      ~ Forest * Year
      ~1,
      y= deer_y,
      det_covs = Year_frame
)

p8 <- auto_occ(
      ~ FireSev + Year
      ~1,
      y= deer_y,
      det_covs = Year_frame
)

p9 <- auto_occ(
      ~ FireSev * Year
      ~1,
      y= deer_y,
      det_covs = Year_frame
)

# Comparing models
detection.aic <- compare_models(
  list(null = pnull,
       Forest = p1,
       FireSev = p2,
       Year = p3,
       `Forest+FireSev` = p4,
       `Forest*FireSev` = p5,
       `Forest+Year` = p6,
       `Forest*Year` =p7,
       `FireSev+Year` = p8,
       `FireSev*Year` = p9),
  digits = 2
)

dfsd <- detection.aic
dfsd



#write.csv(dfsd, "Deer_FireSev_Detection.csv")
### Best model is model 7 Forest * Year acounting for 97% of the weight

```

Occupancy response to fire severity across fire types

```{r}


q2 <- auto_occ(
  ~Forest * Year
  ~ Forest * FireSev,
  y = deer_y,
  det_covs = Year_frame,
  occ_covs = Year_frame
)

summary(q2)

q2_b <- summary(q2)

dq2_b <- q2_b@rho
oq2_b <- q2_b@psi

write.csv(dq2_b, "Det_Deer_Q2_Betas.csv")
write.csv(oq2_b, "Occ_Deer_Q2_Betas.csv")

# nd1 <- data.frame(Forest= "A", Fire=as.factor(1), years=c(2:5), effort=14)
# nd2 <- data.frame(Forest= "A", Fire=as.factor(0), years=c(2:5), effort=14)
# nd3 <- data.frame(Forest= "J", Fire=as.factor(1), years=c(2:5), effort=14)
# nd4 <- data.frame(Forest= "J", Fire=as.factor(0), years=c(2:5), effort=14)
# nd5 <- data.frame(Forest= "M", Fire=as.factor(1), years=c(2:5), effort=14)
# nd6 <- data.frame(Forest= "M", Fire=as.factor(0), years=c(2:5), effort=14)
# 
# nd <- rbind(nd1,nd2,nd3,nd4,nd5,nd6)
# nd

nd1 <- data.frame(Forest= "A", FireSev = c(0:4))

nd3 <- data.frame(Forest= "J", FireSev= c(0:4))

nd5 <- data.frame(Forest= "M", FireSev = c(0:4))


nd <- rbind(nd1,nd3,nd5)
nd

q2.predict <- predict(q2, type = "psi", newdata = nd)
q2.predict <- cbind(nd, q2.predict)
q2.predict





ggplot(data = q2.predict, aes(y= estimate, x= FireSev, colour = Forest))+
  geom_smooth()+
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.1, linetype = "dashed", fill = "white")+
  theme_classic()+
  ylab("Deer Occupancy")+
  xlab("Fire Severity")+
  labs(color = "Forest Type")+
  scale_color_manual(values = c("A" = "#FFCC33", "M"= "red", "J"= "darkgreen"),label = c("Aspen Conifer", 
                            "Pinyon Juniper",
                            "Oak Maple"))+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text   = element_text(size=12, family = "serif", colour = "black"),
        legend.title  = element_text(size=12, family = "serif", colour = "black"),
        panel.border  = element_blank())+
  scale_y_continuous(limits = c(0, 1))

# Rpeat no legend

ggplot(data = q2.predict, aes(y= estimate, x= FireSev, colour = Forest))+
  geom_smooth()+
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.1, linetype = "dashed", fill = "white")+
  theme_classic()+
  ylab("Deer Occupancy")+
  xlab("Fire Severity")+
  labs(color = "Forest Type")+
  scale_color_manual(values = c("A" = "#FFCC33", "M"= "red", "J"= "darkgreen"),label = c("Aspen Conifer", 
                            "Pinyon Juniper",
                            "Oak Maple"))+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text   = element_text(size=12, family = "serif", colour = "black"),
        legend.title  = element_text(size=12, family = "serif", colour = "black"),
        panel.border  = element_blank())+
  scale_y_continuous(limits = c(0, 1))+ 
  theme(legend.position = "none")

```


Question 3
How does occupancy vary across time in burned areas across forest types?
This is where model selection comes in 

Fitting models

```{r}



# make named list (don't worry about the warning)
Year_frame <- list(
   Year = matrix(
     dh$Year,
     ncol = dim(deer_y)[2],
     nrow = dim(deer_y)[1]
   ),
   Forest = deer_covariates$Forest,
   Fire = deer_covariates$Fire,
   Season = matrix(seasons,
                   ncol = dim(deer_y)[2],
     nrow = dim(deer_y)[1])
 )


### Lets find the best occupancy model

# Find best occupancy model
psinull <- auto_occ(
      ~ Forest* Year
      ~1,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi1 <- auto_occ(
      ~ Forest* Year
      ~ Forest,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi2 <- auto_occ(
      ~ Forest* Year
      ~ Fire,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi3 <- auto_occ(
      ~ Forest* Year
      ~ Year,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)




psi4 <- auto_occ(
      ~ Forest* Year
      ~ Forest + Fire,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



psi5 <- auto_occ(
      ~ Forest* Year
      ~ Forest * Fire,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi6 <- auto_occ(
      ~ Forest* Year
      ~ Forest + Year,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi7 <- auto_occ(
      ~ Forest* Year
      ~ Forest * Year,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi8 <- auto_occ(
      ~ Forest* Year
      ~ Fire + Year,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi9 <- auto_occ(
      ~ Forest* Year
      ~ Fire * Year,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



# Comparing models
psi.aic <- compare_models(
  list(null = psinull,
       Forest = psi1,
       Fire = psi2,
       Year = psi3,
       `Forest+Fire` = psi4,
       `Forest*Fire` = psi5,
       `Forest+Year` = psi6,
       `Forest*Year` =psi7,
       `Fire+Year` = psi8,
       `Fire*Year` = psi9),
  digits = 2
)

dfb <- summary(psi7)
dfb

ddfb <- dfb@rho
odfb <- dfb@psi

typeof(dfb)

write.csv(ddfb, "Det_Deer_Fire_Betas.csv")
write.csv(odfb, "Occ_Deer_Fire_Betas.csv")

psi.aic

### Plot best model
summary(psi7)
bdf <- predict(psi7, type = "psi")
bdf

ggplot(data = bdf, aes(x= Year, y= estimate, colour = Forest))+
  geom_smooth()+
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.1, linetype = "dashed", fill = "white")+
  ylab("Deer Occupancy")+
  theme_classic()+
  scale_color_manual(values = c("A" = "#FFCC33", "M"= "red", "J"= "darkgreen"),label = c("Aspen Conifer", 
                            "Pinyon Juniper",
                            "Oak Maple"))+
  theme(
    text = element_text(family = "serif", size = 12, color = "black"),
    axis.title = element_text(size = 12, color = "black"),
    axis.text = element_text(size = 12, color = "black"),
    legend.text = element_text(size = 12, color = "black"),
    legend.title = element_text(size = 12, color = "black"),
    plot.title = element_text(size = 12, color = "black"),
    plot.subtitle = element_text(size = 12, color = "black"),
    plot.caption = element_text(size = 12, color = "black")
  )

# Rerun without legend

ggplot(data = bdf, aes(x= Year, y= estimate, colour = Forest))+
  geom_smooth()+
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.1, linetype = "dashed", fill = "white")+
  ylab("Deer Occupancy")+
  theme_classic()+
  scale_color_manual(values = c("A" = "#FFCC33", "M"= "red", "J"= "darkgreen"),label = c("Aspen Conifer", 
                            "Pinyon Juniper",
                            "Oak Maple"))+
  theme(
    text = element_text(family = "serif", size = 12, color = "black"),
    axis.title = element_text(size = 12, color = "black"),
    axis.text = element_text(size = 12, color = "black"),
    legend.text = element_text(size = 12, color = "black"),
    legend.title = element_text(size = 12, color = "black"),
    plot.title = element_text(size = 12, color = "black"),
    plot.subtitle = element_text(size = 12, color = "black"),
    plot.caption = element_text(size = 12, color = "black")
  )+
  theme(legend.position="none")
  



 dbo <- psi.aic
#write.csv(dbo, "Deer_Burned_Occupancy.csv")

variables <- list(
  Forest = c("Forest*Year", "Forest", "Forest+Fire", "Forest+Year", "Forest*Fire"),
  Year = c("Forest*Year", "Forest+Year", "Year", "Fire+Year", "Fire*Year"),
  Fire = c("Forest+Fire", "Fire", "Forest*Fire", "Fire+Year", "Fire*Year")
)

#### Lots of top competing models

#Calculate relative variable importance

importance<- sapply(variables, function(models){
  sum(psi.aic$AICwt[psi.aic$model %in% models])
})

importance <- as.data.frame(importance)
importance$variable <- row.names(importance)

deer_importance <- importance

ggplot(importance, aes(y = importance, x = variable)) +
  geom_col(size = 3, fill = "blue") +
  geom_text(aes(label = importance), vjust = -0.2, size = 4) +
  labs(y = "Relative Importance (w+)", x = "Variable", 
       title = "Deer Fire") +
  scale_x_discrete(label =c("Fire", "Forest", "Year"))+
  theme_classic() +
  ylim(0, 1)+
  theme(
     text = element_text(family = "serif", size = 12, color = "black"),
    axis.title = element_text(size = 12, color = "black"),
    axis.text = element_text(size = 12, color = "black"),
    legend.text = element_text(size = 12, color = "black"),
    legend.title = element_text(size = 12, color = "black"),
    plot.title = element_text(size = 12, color = "black"),
    plot.subtitle = element_text(size = 12, color = "black"),
    plot.caption = element_text(size = 12, color = "black")
  )+
    scale_y_continuous(expand = c(0, 0), limits = c(0,1))

summary(psinull)

```




Model Averaging

```{r}

# To model average, get the parameters in each model,
# and set up a binary matrix to denote if they were present or not in that model.

# create model list again
model_list <- list(a=psinull,b=psi1,c=psi2,d=psi3,e=psi4,f=psi5,g=psi6,h=psi7, i=psi8, j=psi9)

# and AIC results
aic_results <- compare_models(
  model_list
)

aic_results


# reorder the model_list based on relative fit
model_list <- model_list[aic_results$model]

model_list


aic_results$model
# specify confidence interval width
my_ci_width <- 0.95


# get only the model parameters 
parms <- lapply(
  model_list,
  function(x){
    x@estimates$parameter
  }
)


# select only unique parameters
all_parms <- unique(
  unlist(
    parms
  )
)

# make an empty matrix
parm_matrix <- matrix(
  0,
  ncol = length(
    all_parms
  ),
  nrow = length(
    model_list
  )
)
colnames(parm_matrix) <- all_parms

# Add '1's to models which have parameter present
for(i in 1:nrow(parm_matrix)){
  parm_matrix[i, parms[[i]]] <- 1
}

# calculate overall weight for each parameter. The easiest
#  way to do this is to make a weight matrix.
weight_matrix <- matrix(
  aic_results$AICwt,
  nrow = length(model_list),
  ncol = length(all_parms)
)

parm_weight <- colSums(
  parm_matrix * weight_matrix
)

parm_weight

#  We are going to take samples from the parameters (which
#  is the same thing we do to make predictions
#  via autoOcc::predict). To do that, we need
#  to get the variance covariance matrix
#  for each model.

cov_mat <- lapply(
  model_list,
  vcov
)

# and now the estimates (assuming you are not
# using any offsets in the model for this).

ests <- lapply(
  model_list,
  function(x) x@estimates$Est
)

# do 5000 samples for each parameter.
mvn_samps <- vector(
  "list",
  length = length(model_list)
)
nsim = 5000
set.seed(465)
for(i in 1:length(mvn_samps)){
  mvn_samps[[i]] <- mvtnorm::rmvnorm(
    nsim,
    mean = ests[[i]],
    sigma = cov_mat[[i]],
    method = "svd"
  )
  colnames(mvn_samps[[i]]) <- parms[[i]]
}

# do model averaging for each parameter
avg_parm <- data.frame(
  parameter = all_parms,
  est = NA,
  lower = NA,
  upper = NA
)

for(i in 1:nrow(avg_parm)){
  my_parm <- avg_parm$parameter[i]
  which_models <- which(
    parm_matrix[,i] == 1
  )
  
  weights <- weight_matrix[
    which_models,i
  ] * parm_matrix[
    which_models,i
  ]
  
  # get beta terms
  beta_mat <- matrix(
    NA,
    ncol = length(which_models),
    nrow = nsim
  )
  
  # multiply weight across columns while we do this
  for(j in 1:ncol(beta_mat)){
    beta_mat[,j] <- mvn_samps[[which_models[j]]][,my_parm] *
      weights[j]
  }
  
  # sum each row
  beta_mat <- rowSums(beta_mat)
  
  # divide by overall weight
  beta_mat <- beta_mat / parm_weight[i]
  
  # summarise
  avg_parm$est[i] <- median(beta_mat)
  avg_parm$lower[i] <- quantile(
    beta_mat,
    (1 - my_ci_width) / 2
  )
  avg_parm$upper[i] <- quantile(
    beta_mat,
    1 - ( (1 - my_ci_width) / 2 )
  )
  
}


# get average estimate
avg_parm %>% 
  mutate(
    across(
      where(is.numeric), ~ round(., digits = 2))
    )
  

data_filtered <- avg_parm %>%
  filter(!grepl("^rho", parameter))

data_filtered


ggplot(data= data_filtered, aes(x = est, y = parameter)) +
  geom_point() +
  geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.2) +
  labs(title = "Deer Fire",
       x = "Estimate",
       y = "Parameter") +
  theme_minimal()+
  theme(
    text = element_text(family = "serif", size = 12),
    axis.title = element_text(size = 12, color = "black"),
    axis.text = element_text(size = 12, color = "black"),
    legend.text = element_text(size = 12, color = "black"),
    legend.title = element_text(size = 12, color = "black"),
    plot.title = element_text(size = 12, color = "black"),
    plot.subtitle = element_text(size = 12, color = "black"),
    plot.caption = element_text(size = 12, color = "black")
  )+xlim(-7.5,7.5)


```

Predict occupancy

```{r}


#### Plot best model

nd1 <- data.frame(Forest= "A", Year = c(1:4))

nd3 <- data.frame(Forest= "J", Year = c(1:4))

nd5 <- data.frame(Forest= "M", Year = c(1:4))


nd <- rbind(nd1,nd3,nd5)
nd

pred.top <- predict(psi7, type = "psi", newdata = nd)
pred.top <- cbind(nd, pred.top)

head(pred.top)

ggplot(data = pred.top, aes(y= estimate, x=Year, colour = Forest))+
  geom_point(size = 2, position = position_dodge(0.2))+
  geom_line(position = position_dodge(0.2))+
  geom_errorbar(aes(ymin= lower, ymax = upper, width = 0.2), position = position_dodge(0.2))+
  theme_classic()+
  ylab("Deer Occupancy")+
  theme(text = element_text(family = "serif", size = 12))+
  scale_color_discrete(label = c("Aspen Conifer", 
                             "Pinyon Juniper",
                             "Oak Maple"))+
  theme(
  text = element_text(family = "serif", size = 12, color = "black"),
    axis.title = element_text(size = 12, color = "black"),
    axis.text = element_text(size = 12, color = "black"),
    legend.text = element_text(size = 12, color = "black"),
    legend.title = element_text(size = 12, color = "black"),
    plot.title = element_text(size = 12, color = "black"),
    plot.subtitle = element_text(size = 12, color = "black"),
    plot.caption = element_text(size = 12, color = "black")
  )+
  ylim(0,1)

#rerun without legend

ggplot(data = pred.top, aes(y= estimate, x=Year, colour = Forest))+
  geom_point(size = 2, position = position_dodge(0.2))+
  geom_line(position = position_dodge(0.2))+
  geom_errorbar(aes(ymin= lower, ymax = upper, width = 0.2), position = position_dodge(0.2))+
  theme_classic()+
  ylab("Deer Occupancy")+
  theme(text = element_text(family = "serif", size = 12))+
  scale_color_discrete(label = c("Aspen Conifer", 
                             "Pinyon Juniper",
                             "Oak Maple"))+
  theme(
  text = element_text(family = "serif", size = 12, color = "black"),
    axis.title = element_text(size = 12, color = "black"),
    axis.text = element_text(size = 12, color = "black"),
    legend.text = element_text(size = 12, color = "black"),
    legend.title = element_text(size = 12, color = "black"),
    plot.title = element_text(size = 12, color = "black"),
    plot.subtitle = element_text(size = 12, color = "black"),
    plot.caption = element_text(size = 12, color = "black")
  )+
  ylim(0,1)+
  theme(legend.position="none")

```

Rerun model selection but with Fire Severity

Fitting models

```{r}

# make named list (don't worry about the warning)
Year_frame <- list(
   Year = matrix(
     dh$Year,
     ncol = dim(deer_y)[2],
     nrow = dim(deer_y)[1]
   ),
   Forest = deer_covariates$Forest,
   FireSev = deer_covariates$FireSev
 )


### Lets find the best occupancy model

# Find best occupancy model
psinull <- auto_occ(
      ~ Forest* Year
      ~1,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi1 <- auto_occ(
      ~ Forest* Year
      ~ Forest,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi2 <- auto_occ(
      ~ Forest* Year
      ~ FireSev,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi3 <- auto_occ(
      ~ Forest* Year
      ~ Year,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



psi4 <- auto_occ(
      ~ Forest* Year
      ~ Forest + FireSev,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



psi5 <- auto_occ(
      ~ Forest* Year
      ~ Forest * FireSev,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi6 <- auto_occ(
      ~ Forest* Year
      ~ Forest + Year,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi7 <- auto_occ(
      ~ Forest* Year
      ~ Forest * Year,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi8 <- auto_occ(
      ~ Forest* Year
      ~ FireSev + Year,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi9 <- auto_occ(
      ~ Forest* Year
      ~ FireSev * Year,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

# Comparing models
psi.aic <- compare_models(
  list(null = psinull,
       Forest = psi1,
       Fire = psi2,
       Year = psi3,
       `Forest+FireSev` = psi4,
       `Forest*FireSev` = psi5,
       `Forest+Year` = psi6,
       `Forest*Year` =psi7,
       `FireSev+Year` = psi8,
       `FireSev*Year` = psi9),
  digits = 2
)

psi.aic



dfsb <-summary(psi7)

ddfsb <- dfsb@rho
odfsb <- dfsb@psi

write.csv(ddfsb, "Det_Deer_FireSev_Betas.csv")
write.csv(odfsb, "Occ_Deer_FireSev_Betas.csv")

### Plot best model
bdfs <- predict(psi7, type = "psi")
bdfs

#### Iteration 1####
ggplot(data = bdfs, aes(x= Year, y= estimate, colour = Forest))+
  geom_smooth()+
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.1, linetype = "dashed", fill = "white")+
  theme_classic()+
  ylab("Deer Occupancy")+
  labs(color = "Forest Type")+
  scale_color_manual(values = c("A" = "#FFCC33", "M"= "red", "J"= "darkgreen"),label = c("Aspen Conifer", 
                            "Pinyon Juniper",
                            "Oak Maple"))+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text   = element_text(size=12, family = "serif", colour = "black"),
        legend.title  = element_text(size=12, family = "serif", colour = "black"),
        panel.border  = element_blank())+
  scale_y_continuous(limits = c(0, 1))


#####ITeration 2 #####

ggplot(data = bdfs[bdfs$Forest!= "J",], aes(x= Year, y= estimate, colour = Forest))+
  geom_smooth()+
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.1, linetype = "dashed", fill = "white")+
  theme_classic()+
  ylab("Deer Occupancy")+
  labs(color = "Forest Type")+
  scale_color_manual(values = c("A" = "#FFCC33", "M"= "red"),label = c("Aspen Conifer", 
                            "Oak Maple",
                            "Pinyon Juniper"))+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text   = element_text(size=12, family = "serif", colour = "black"),
        legend.title  = element_text(size=12, family = "serif", colour = "black"),
        panel.border  = element_blank())+
  scale_y_continuous(limits = c(0, 1))

#### Iteration 3 #####

ggplot(data = bdfs[bdfs$Forest== "A",], aes(x= Year, y= estimate, colour = Forest))+
  geom_smooth()+
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.1, linetype = "dashed", fill = "white")+
  theme_classic()+
  ylab("Deer Occupancy")+
  labs(color = "Forest Type")+
  scale_color_manual(values = c("A"= "#FFCC33"),label = c("Aspen Conifer", 
                             "Pinyon Juniper",
                             "Oak Maple"))+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text   = element_text(size=12, family = "serif", colour = "black"),
        legend.title  = element_text(size=12, family = "serif", colour = "black"),
        panel.border  = element_blank())+
  scale_y_continuous(limits = c(0, 1))

###############

dfso <- psi.aic
#write.csv(dfso, "Deer_FireSev_Occupancy.csv")

variables <- list(
  Forest = c("Forest*Year", "Forest", "Forest+Fire", "Forest+Year", "Forest*Fire"),
  Year = c("Forest*Year", "Forest+Year", "Year", "Fire+Year", "Fire*Year"),
  `Fire Severity` = c("Forest+Fire", "Fire", "Forest*Fire", "Fire+Year", "Fire*Year")
)

#### Lots of top competing models

#Calculate relative variable importance

importance<- sapply(variables, function(models){
  sum(psi.aic$AICwt[psi.aic$model %in% models])
})

importance <- as.data.frame(importance)
importance$variable <- row.names(importance)


ggplot(importance, aes(y = importance, x = variable)) +
  geom_col(size = 3, fill = "blue") +
  geom_text(aes(label = importance), vjust = -0.2, size = 4) +
  labs(y = "Relative Importance (w+)", x = "Variable", 
       title = "Deer Fire Severity") +
  scale_x_discrete(label =c("Fire\nSeverity", "Forest", "Year"))+
  theme_classic() +
  ylim(0, 1)+
  theme(
     text = element_text(family = "serif", size = 12, color = "black"),
    axis.title = element_text(size = 12, color = "black"),
    axis.text = element_text(size = 12, color = "black"),
    legend.text = element_text(size = 12, color = "black"),
    legend.title = element_text(size = 12, color = "black"),
    plot.title = element_text(size = 12, color = "black"),
    plot.subtitle = element_text(size = 12, color = "black"),
    plot.caption = element_text(size = 12, color = "black")
  )+
    scale_y_continuous(expand = c(0, 0), limits = c(0,1))

## Final best prediction without legend

ggplot(data = bdfs, aes(x= Year, y= estimate, colour = Forest))+
  geom_smooth()+
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.1, linetype = "dashed", fill = "white")+
  theme_classic()+
  ylab("Deer Occupancy")+
  labs(color = "Forest Type")+
  scale_color_manual(values = c("A" = "#FFCC33", "M"= "red", "J"= "darkgreen"),label = c("Aspen Conifer", 
                            "Pinyon Juniper",
                            "Oak Maple"))+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text   = element_text(size=12, family = "serif", colour = "black"),
        legend.title  = element_text(size=12, family = "serif", colour = "black"),
        panel.border  = element_blank())+
  scale_y_continuous(limits = c(0, 1))+
  theme(legend.position = "none")

```

Model Averaging

```{r}

# To model average, get the parameters in each model,
# and set up a binary matrix to denote if they were present or not in that model.

# create model list again
model_list <- list(a=psinull,b=psi1,c=psi2,d=psi3,e=psi4,f=psi5,g=psi6,h=psi7, i=psi8, j=psi9)

# and AIC results
aic_results <- compare_models(
  model_list
)

aic_results



# reorder the model_list based on relative fit
model_list <- model_list[aic_results$model]

model_list


aic_results$model
# specify confidence interval width
my_ci_width <- 0.95


# get only the model parameters 
parms <- lapply(
  model_list,
  function(x){
    x@estimates$parameter
  }
)


# select only unique parameters
all_parms <- unique(
  unlist(
    parms
  )
)

# make an empty matrix
parm_matrix <- matrix(
  0,
  ncol = length(
    all_parms
  ),
  nrow = length(
    model_list
  )
)
colnames(parm_matrix) <- all_parms

# Add '1's to models which have parameter present
for(i in 1:nrow(parm_matrix)){
  parm_matrix[i, parms[[i]]] <- 1
}

# calculate overall weight for each parameter. The easiest
#  way to do this is to make a weight matrix.
weight_matrix <- matrix(
  aic_results$AICwt,
  nrow = length(model_list),
  ncol = length(all_parms)
)

parm_weight <- colSums(
  parm_matrix * weight_matrix
)

parm_weight

#  We are going to take samples from the parameters (which
#  is the same thing we do to make predictions
#  via autoOcc::predict). To do that, we need
#  to get the variance covariance matrix
#  for each model.

cov_mat <- lapply(
  model_list,
  vcov
)

# and now the estimates (assuming you are not
# using any offsets in the model for this).

ests <- lapply(
  model_list,
  function(x) x@estimates$Est
)

# do 5000 samples for each parameter.
mvn_samps <- vector(
  "list",
  length = length(model_list)
)
nsim = 5000
set.seed(465)
for(i in 1:length(mvn_samps)){
  mvn_samps[[i]] <- mvtnorm::rmvnorm(
    nsim,
    mean = ests[[i]],
    sigma = cov_mat[[i]],
    method = "svd"
  )
  colnames(mvn_samps[[i]]) <- parms[[i]]
}

# do model averaging for each parameter
avg_parm <- data.frame(
  parameter = all_parms,
  est = NA,
  lower = NA,
  upper = NA
)

for(i in 1:nrow(avg_parm)){
  my_parm <- avg_parm$parameter[i]
  which_models <- which(
    parm_matrix[,i] == 1
  )
  
  weights <- weight_matrix[
    which_models,i
  ] * parm_matrix[
    which_models,i
  ]
  
  # get beta terms
  beta_mat <- matrix(
    NA,
    ncol = length(which_models),
    nrow = nsim
  )
  
  # multiply weight across columns while we do this
  for(j in 1:ncol(beta_mat)){
    beta_mat[,j] <- mvn_samps[[which_models[j]]][,my_parm] *
      weights[j]
  }
  
  # sum each row
  beta_mat <- rowSums(beta_mat)
  
  # divide by overall weight
  beta_mat <- beta_mat / parm_weight[i]
  
  # summarise
  avg_parm$est[i] <- median(beta_mat)
  avg_parm$lower[i] <- quantile(
    beta_mat,
    (1 - my_ci_width) / 2
  )
  avg_parm$upper[i] <- quantile(
    beta_mat,
    1 - ( (1 - my_ci_width) / 2 )
  )
  
}


# get average estimate
avg_parm %>% 
  mutate(
    across(
      where(is.numeric), ~ round(., digits = 2))
    )
  
avg_parm

data_filtered <- avg_parm %>%
  filter(!grepl("^rho", parameter))

data_filtered

ggplot(data= data_filtered, aes(x = est, y = parameter)) +
  geom_point() +
  geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.2) +
  labs(title = "Deer Fire Severity",
       x = "Estimate",
       y = "Parameter") +
  theme_minimal()+
  theme(
     text = element_text(family = "serif", size = 12, color = "black"),
    axis.title = element_text(size = 12, color = "black"),
    axis.text = element_text(size = 12, color = "black"),
    legend.text = element_text(size = 12, color = "black"),
    legend.title = element_text(size = 12, color = "black"),
    plot.title = element_text(size = 12, color = "black"),
    plot.subtitle = element_text(size = 12, color = "black"),
    plot.caption = element_text(size = 12, color = "black")
  )+xlim(-7.5,7.5)

```



Predict occupancy

```{r}


#### Plot best model

nd1 <- data.frame(Forest= "A", Year = c(1:4))

nd3 <- data.frame(Forest= "J", Year = c(1:4))

nd5 <- data.frame(Forest= "M", Year = c(1:4))


nd <- rbind(nd1,nd3,nd5)
nd

pred.top <- predict(psi7, type = "psi", newdata = nd)
pred.top <- cbind(nd, pred.top)


ggplot(data = pred.top, aes(y= estimate, x=Year, colour = Forest))+
  geom_point(size = 2, position = position_dodge(0.2))+
  geom_line(position = position_dodge(0.2))+
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, position = position_dodge(0.2))+
  theme_classic()+
  ylab("Deer Occupancy")+
  theme(text = element_text(family = "serif", size = 12))+
  scale_color_discrete(label = c("Aspen Conifer", 
                             "Pinyon Juniper",
                             "Oak Maple"))+
  theme(
 text = element_text(family = "serif", size = 12, color = "black"),
    axis.title = element_text(size = 12, color = "black"),
    axis.text = element_text(size = 12, color = "black"),
    legend.text = element_text(size = 12, color = "black"),
    legend.title = element_text(size = 12, color = "black"),
    plot.title = element_text(size = 12, color = "black"),
    plot.subtitle = element_text(size = 12, color = "black"),
    plot.caption = element_text(size = 12, color = "black")
  )+
  ylim(0,1)

# Rerun without legend

ggplot(data = pred.top, aes(y= estimate, x=Year, colour = Forest))+
  geom_point(size = 2, position = position_dodge(0.2))+
  geom_line(position = position_dodge(0.2))+
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, position = position_dodge(0.2))+
  theme_classic()+
  ylab("Deer Occupancy")+
  theme(text = element_text(family = "serif", size = 12))+
  scale_color_discrete(label = c("Aspen Conifer", 
                             "Pinyon Juniper",
                             "Oak Maple"))+
  theme(
 text = element_text(family = "serif", size = 12, color = "black"),
    axis.title = element_text(size = 12, color = "black"),
    axis.text = element_text(size = 12, color = "black"),
    legend.text = element_text(size = 12, color = "black"),
    legend.title = element_text(size = 12, color = "black"),
    plot.title = element_text(size = 12, color = "black"),
    plot.subtitle = element_text(size = 12, color = "black"),
    plot.caption = element_text(size = 12, color = "black")
  )+
  ylim(0,1)+
  theme(legend.position = "none")

```

Isolate features to compare to the global model

```{r, fig.width=5,fig.height=4}

# make named list (don't worry about the warning)
Year_frame <- list(
   Year = matrix(
     dh$Year,
     ncol = dim(deer_y)[2],
     nrow = dim(deer_y)[1]
   ),
   Forest = deer_covariates$Forest,
   Fire = deer_covariates$Fire
 )

### Start with the interactions
all.int <- auto_occ(
      ~ Forest* Fire
      ~ Forest * Year * Fire,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

all.add <- auto_occ(
      ~ Forest* Fire
      ~ Forest + Year + Fire,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)


predict.int <- predict(all.int, type = "psi")
predict.add <- predict(all.add, type = "psi")

ggplot(data = predict.int, aes(x = Year, y= estimate, colour = Forest, shape = Fire))+ 
  geom_point(size =3)+ 
  geom_line()+
  theme_classic()

ggplot(data = predict.add, aes(x = Year, y= estimate, colour = Forest, shape = Fire))+ 
  geom_point(size =3)+ 
  geom_line()+
  theme_classic()

dh.sub <- dh
dh.sub$Forest <- substr(dh.sub$site,5,5)
dh.sub$Fire <- substr(dh.sub$site,7,7)

aspen_y <- format_y(
  x = dh.sub[dh.sub$Forest == "A",],
  site_column = "site",
  time_column = "Year",
  history_columns = 1:25
)

aspen.covariates <- deer_covariates[deer_covariates$Forest=="A",]

### Test some models

#aspen
a1 <- auto_occ(
      ~1
      ~1,
      y= aspen_y)

aspen_frame <- list(
   Year = matrix(c(rep(1, 12), rep(2, 12), rep(3, 12), rep(4, 12)), nrow = 12, ncol = 4),
   Fire = aspen.covariates$Fire
 )

a7 <- auto_occ(
      ~ Fire
      ~ Year * Fire,
      y= aspen_y,
      det_covs = aspen_frame,
      occ_covs = aspen_frame
)

aspen <- predict(a7, type = "psi")
aspen

ggplot(data = aspen, aes(x= Year, y = estimate, shape = Fire))+
  geom_point(size = 3)+
  geom_line()+ 
  theme_classic()

#juniper

juniper_y <- format_y(
  x = dh.sub[dh.sub$Forest == "J",],
  site_column = "site",
  time_column = "Year",
  history_columns = 1:25
)

juniper.covariates <- deer_covariates[deer_covariates$Forest=="J",]


j1 <- auto_occ(
      ~1
      ~1,
      y= juniper_y)

juniper_frame <- list(
   Year = matrix(c(rep(1, 12), rep(2, 12), rep(3, 12), rep(4, 12)), nrow = 12, ncol = 4),
   Fire = juniper.covariates$Fire
 )

j7 <- auto_occ(
      ~ Fire
      ~ Year * Fire,
      y= juniper_y,
      det_covs = aspen_frame,
      occ_covs = aspen_frame
)

juniper <- predict(j7, type = "psi")
juniper

ggplot(data = juniper, aes(x= Year, y = estimate, shape = Fire))+
  geom_point(size = 3)+
  geom_line()+ 
  theme_classic()


### Lets try this now with fire

burned_y <- format_y(
  x = dh.sub[dh.sub$Fire == 1,],
  site_column = "site",
  time_column = "Year",
  history_columns = 1:25
)

burned.covariates <- deer_covariates[deer_covariates$Fire==1,]

### Test some models

#aspen
b1 <- auto_occ(
      ~1
      ~1,
      y= burned_y)

burned_frame <- list(
   Year = matrix(c(rep(1, 12), rep(2, 12), rep(3, 12), rep(4, 12)), nrow = 16, ncol = 4),
   Forest = burned.covariates$Forest
 )

b7 <- auto_occ(
      ~ Forest
      ~ Year * Forest,
      y= burned_y,
      det_covs = burned_frame,
      occ_covs = burned_frame
)

burned <- predict(b7, type = "psi")
burned

ggplot(data = burned, aes(x= Year, y = estimate, color = Forest))+
  geom_point(size = 3)+
  geom_line()+ 
  theme_classic()



```

Best occupancy without accounting for detection
ie p ~ 1

```{r}


# make named list (don't worry about the warning)
Year_frame <- list(
   Year = matrix(
     dh$Year,
     ncol = dim(deer_y)[2],
     nrow = dim(deer_y)[1]
   ),
   Forest = deer_covariates$Forest,
   Fire = deer_covariates$Fire,
   Season = matrix(seasons,
                   ncol = dim(deer_y)[2],
     nrow = dim(deer_y)[1])
 )


### Lets find the best occupancy model

# Find best occupancy model
onull <- auto_occ(
      ~ 1
      ~1,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

o1 <- auto_occ(
      ~ 1
      ~ Forest,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

o2 <- auto_occ(
      ~ 1
      ~ Fire,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

o3 <- auto_occ(
      ~ 1
      ~ Year,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)




o4 <- auto_occ(
      ~ 1
      ~ Fire + Forest,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



o5 <- auto_occ(
      ~ 1
      ~ Fire * Forest,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

o6 <- auto_occ(
      ~ 1
      ~ Fire + Year,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

o7 <- auto_occ(
      ~ 1
      ~ Fire * Year,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

o8 <- auto_occ(
      ~ 1
      ~ Forest + Year,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

o9 <- auto_occ(
      ~ 1
      ~ Forest * Year,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)


# Comparing models
o.aic <- compare_models(
  list(null = onull,
       Forest = o1,
       Fire = o2,
       Year = o3,
       `Fire+Forest` = o4,
       `Fire*Forest` = o5,
       `Fire+Year` = o6,
       `Fire*Year` = o7,
       `Forest+Year` = o8,
       `Forest*Year` = o9),
  digits = 2
)

o.aic

variables <- list(
  Forest = c("Forest*Year", "Forest", "Forest+Fire", "Forest+Year", "Forest*Fire"),
  Year = c("Forest*Year", "Forest+Year", "Year", "Fire+Year", "Fire*Year"),
  Fire = c("Forest+Fire", "Fire", "Forest*Fire", "Fire+Year", "Fire*Year")
)

#### Lots of top competing models

#Calculate relative variable importance

importance<- sapply(variables, function(models){
  sum(o.aic$AICwt[o.aic$model %in% models])
})

importance <- as.data.frame(importance)
importance$variable <- row.names(importance)


ggplot(importance, aes(x = importance, y = variable)) +
  geom_point(size = 3, color = "blue") +
  geom_text(aes(label = importance), hjust = -0.2, size = 4) +
  labs(x = "Relative Importance (w+)", y = "Variable", 
       title = "Relative Variable Importance") +
  theme_classic() +
  xlim(0, 1)+
  theme(
   text = element_text(family = "serif", size = 12, color = "black"),
    axis.title = element_text(size = 12, color = "black"),
    axis.text = element_text(size = 12, color = "black"),
    legend.text = element_text(size = 12, color = "black"),
    legend.title = element_text(size = 12, color = "black"),
    plot.title = element_text(size = 12, color = "black"),
    plot.subtitle = element_text(size = 12, color = "black"),
    plot.caption = element_text(size = 12, color = "black")
  )



```


Now break it down by seasons

First check the differences between seasons

```{r}

psis1 <- auto_occ(
      ~ 1
      ~ Season,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

pred.season <- predict(psis1, type = "psi")

ggplot(data = pred.season, aes(y= estimate, x=Season))+
  geom_col()+
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, position = position_dodge(0.2))+
  theme_classic()+
  ylab("Deer Occupancy")+
  theme(text = element_text(family = "serif", size = 12))+
  theme(
 text = element_text(family = "serif", size = 12, color = "black"),
    axis.title = element_text(size = 12, color = "black"),
    axis.text = element_text(size = 12, color = "black"),
    legend.text = element_text(size = 12, color = "black"),
    legend.title = element_text(size = 12, color = "black"),
    plot.title = element_text(size = 12, color = "black"),
    plot.subtitle = element_text(size = 12, color = "black"),
    plot.caption = element_text(size = 12, color = "black")
  )+
  ylim(0,1)

```


Now do season with forest

```{r}

psisf1 <- auto_occ(
      ~ 1
      ~ Season + Forest,
      y= deer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

summary(psisf1)

pred.sf <- predict(psisf1, type = "psi")

pred.sf

ggplot(data = pred.sf, aes(y= estimate, x=Season, fill = Forest))+
  geom_col(position = position_dodge(0.9))+
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, position = position_dodge(0.9))+
  theme_classic()+
  ylab("Deer Occupancy")+
  theme(text = element_text(family = "serif", size = 12))+
  theme(
 text = element_text(family = "serif", size = 12, color = "black"),
    axis.title = element_text(size = 12, color = "black"),
    axis.text = element_text(size = 12, color = "black"),
    legend.text = element_text(size = 12, color = "black"),
    legend.title = element_text(size = 12, color = "black"),
    plot.title = element_text(size = 12, color = "black"),
    plot.subtitle = element_text(size = 12, color = "black"),
    plot.caption = element_text(size = 12, color = "black")
  )+
  ylim(0,1)

```

Isolate seasons and run occupancy models seperately

```{r}

dh

# make named list (don't worry about the warning)
Year_frame <- list(
   Year = matrix(
     dh$Year,
     ncol = dim(deer_y)[2],
     nrow = dim(deer_y)[1]
   ),
   Forest = deer_covariates$Forest,
   Fire = deer_covariates$Fire,
   Season = matrix(seasons,
                   ncol = dim(deer_y)[2],
     nrow = dim(deer_y)[1])
                   
 )

Year_frame

seasons_dh <- DetHist1$detection_history
colnames(seasons_dh) <- seasons
head(seasons_dh)

###### Find seasons correctly #######

# Use seasons dh
summer_positions <- which(seasons == "Summer")

summer_dh <- DetHist1$detection_history[,summer_positions]
summer_dh

s1 <- summer_dh[,1:9]

s2 <- summer_dh[,10:18]

s3 <- summer_dh[,19:27]

s4 <- summer_dh[,28:33]

# Make s4 the same length as the others
s4 <- cbind(s4,matrix(NA,nrow = 32, ncol = 3))


summer_dh <- rbind(s1,s2,s3,s4)


summer_dh <- as.data.frame(summer_dh)
summer_dh$Year<- sequence
summer_dh$site <- substr(row.names(summer_dh),1,9)

summer_y <- format_y(
  x = summer_dh,
  site_column = "site",
  time_column = "Year", 
  history_columns = 1:9
)

head(summer_y)

#### Subset only winter detection histories ####

winter_positions <- which(seasons == "Winter")

winter_dh <- DetHist1$detection_history[,winter_positions]
winter_dh

s1 <- winter_dh[,1:9]

s2 <- winter_dh[,10:18]

s3 <- winter_dh[,19:27]

s4 <- winter_dh[,28:35] ## More winters than summers cos of when we collected

# Make s4 the same length as the others
s4 <- cbind(s4,matrix(NA,nrow = 32, ncol = 1))


winter_dh <- rbind(s1,s2,s3,s4)


winter_dh <- as.data.frame(winter_dh)
winter_dh$Year<- sequence
winter_dh$site <- substr(row.names(winter_dh),1,9)

winter_y <- format_y(
  x = winter_dh,
  site_column = "site",
  time_column = "Year", 
  history_columns = 1:9
)

head(winter_y)

#### Subset only fall detection histories ####

fall_positions <- which(seasons == "Fall")

fall_dh <- DetHist1$detection_history[,fall_positions]
fall_dh

s1 <- fall_dh[,1:3]

s2 <- fall_dh[,4:7]

s3 <- fall_dh[,8:11]

s4 <- fall_dh[,12:16] 

# Make s1 the same length as the others
s1 <- cbind(s1,matrix(NA,nrow = 32, ncol = 2))
s2 <- cbind(s2,matrix(NA,nrow = 32, ncol = 1))
s3 <- cbind(s3,matrix(NA,nrow = 32, ncol = 1))

fall_dh <- rbind(s1,s2,s3,s4)


fall_dh <- as.data.frame(fall_dh)
fall_dh$Year<- sequence
fall_dh$site <- substr(row.names(fall_dh),1,9)

fall_y <- format_y(
  x = fall_dh,
  site_column = "site",
  time_column = "Year", 
  history_columns = 1:4
)

head(fall_y)

#### Subset only spring detection histories ####

spring_positions <- which(seasons == "Spring")

spring_dh <- DetHist1$detection_history[,spring_positions]
spring_dh

s1 <- spring_dh[,1:4]

s2 <- spring_dh[,5:8]

s3 <- spring_dh[,9:12]

s4 <- spring_dh[,13:16] ## More winters than summers cos of when we collected


spring_dh <- rbind(s1,s2,s3,s4)


spring_dh <- as.data.frame(spring_dh)
spring_dh$Year<- sequence
spring_dh$site <- substr(row.names(spring_dh),1,9)

spring_y <- format_y(
  x = spring_dh,
  site_column = "site",
  time_column = "Year", 
  history_columns = 1:4
)

head(spring_y)




```

Rerun model selections on each season
# Start with summer

```{r}

# Find best detection model

p.sum.d.null <- auto_occ(
      ~ 1
      ~1,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.sum.d.1 <- auto_occ(
      ~ Forest
      ~ 1,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.sum.d.2 <- auto_occ(
      ~ Fire
      ~ 1,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.sum.d.3 <- auto_occ(
      ~ Year
      ~ 1,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



p.sum.d.4 <- auto_occ(
      ~ Forest + Fire
      ~ 1,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



p.sum.d.5 <- auto_occ(
      ~ Forest* Fire
      ~ 1,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.sum.d.6 <- auto_occ(
      ~ Forest + Year
      ~ 1,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.sum.d.7 <- auto_occ(
      ~ Forest* Year
      ~ 1,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.sum.d.8 <- auto_occ(
      ~ Fire + Year
      ~ 1,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.sum.d.9 <- auto_occ(
      ~ Fire * Year
      ~ 1,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

# Comparing models
p.sum.d..aic <- compare_models(
  list(null = p.sum.d.null,
       Forest = p.sum.d.1,
       Fire = p.sum.d.2,
       Year = p.sum.d.3,
       `Forest+Fire` = p.sum.d.4,
       `Forest*Fire` = p.sum.d.5,
       `Forest+Year` = p.sum.d.6,
       `Forest*Year` =p.sum.d.7,
       `Fire+Year` = p.sum.d.8,
       `Fire*Year` = p.sum.d.9),
  digits = 2
)

p.sum.d..aic

write.csv(p.sum.d..aic, "Det_Deer_Fire_Summer.csv")

# Find best occupancy model
psi.sum.d.null <- auto_occ(
      ~ Forest* Fire
      ~1,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.sum.d.1 <- auto_occ(
      ~ Forest* Fire
      ~ Forest,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.sum.d.2 <- auto_occ(
      ~ Forest* Fire
      ~ Fire,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.sum.d.3 <- auto_occ(
      ~ Forest* Fire
      ~ Year,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



psi.sum.d.4 <- auto_occ(
      ~ Forest* Fire
      ~ Forest + Fire,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



psi.sum.d.5 <- auto_occ(
      ~ Forest* Fire
      ~ Forest * Fire,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.sum.d.6 <- auto_occ(
      ~ Forest* Fire
      ~ Forest + Year,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.sum.d.7 <- auto_occ(
      ~ Forest* Fire
      ~ Forest * Year,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.sum.d.8 <- auto_occ(
      ~ Forest* Fire
      ~ Fire + Year,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.sum.d.9 <- auto_occ(
      ~ Forest* Fire
      ~ Fire * Year,
      y= summer_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

# Comparing models
psi.sum.d..aic <- compare_models(
  list(null = psi.sum.d.null,
       Forest = psi.sum.d.1,
       Fire = psi.sum.d.2,
       Year = psi.sum.d.3,
       `Forest+Fire` = psi.sum.d.4,
       `Forest*Fire` = psi.sum.d.5,
       `Forest+Year` = psi.sum.d.6,
       `Forest*Year` =psi.sum.d.7,
       `Fire+Year` = psi.sum.d.8,
       `Fire*Year` = psi.sum.d.9),
  digits = 2
)

psi.sum.d..aic
## 7 is best model

#Model prediction

pred.deer.sum <- predict(psi.sum.d.7, type = "psi")

head(pred.deer.sum)

sum_b <- summary(psi.sum.d.7)

dsum_b <- sum_b@rho
osum_b <- sum_b@psi

write.csv(dsum_b, "Det_Deer_Summer_Betas.csv")
write.csv(osum_b, "Occ_Deer_Summer_Betas.csv")

ggplot(data = pred.deer.sum, aes(y= estimate, x= Year, colour = Forest))+
  geom_smooth()+
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.1, linetype = "dashed", fill = "white")+
  theme_classic()+
  ylab("Deer Occupancy")+
  labs(color = "Forest Type")+
  scale_color_manual(values = c("A" = "#FFCC33", "M"= "red", "J"= "darkgreen"),label = c("Aspen Conifer", 
                            "Pinyon Juniper",
                            "Oak Maple"))+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text   = element_text(size=12, family = "serif", colour = "black"),
        legend.title  = element_text(size=12, family = "serif", colour = "black"),
        panel.border  = element_blank())+
  scale_y_continuous(limits = c(0, 1))

# Rerun without legend
ggplot(data = pred.deer.sum, aes(y= estimate, x= Year, colour = Forest))+
  geom_smooth()+
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.1, linetype = "dashed", fill = "white")+
  theme_classic()+
  ylab("Summer Deer Occupancy")+
  labs(color = "Forest Type")+
  scale_color_manual(values = c("A" = "#FFCC33", "M"= "red", "J"= "darkgreen"),label = c("Aspen Conifer", 
                            "Pinyon Juniper",
                            "Oak Maple"))+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text   = element_text(size=12, family = "serif", colour = "black"),
        legend.title  = element_text(size=12, family = "serif", colour = "black"),
        panel.border  = element_blank())+
  scale_y_continuous(limits = c(0, 1))+
  theme(legend.position = "none")

write.csv(psi.sum.d..aic, "Occ_Deer_Fire_Summer.csv")

```

# Winter only occupancy

```{r}

# Find best detection model

# Find best occupancy model
p.win.d.null <- auto_occ(
      ~ 1
      ~1,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.wind.1 <- auto_occ(
      ~ Forest
      ~ 1,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.wind.2 <- auto_occ(
      ~ Fire
      ~ 1,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.wind.3 <- auto_occ(
      ~ Year
      ~ 1,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



p.wind.4 <- auto_occ(
      ~ Forest + Fire
      ~ 1,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



p.wind.5 <- auto_occ(
      ~ Forest* Fire
      ~ 1,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.wind.6 <- auto_occ(
      ~ Forest + Year
      ~ 1,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.wind.7 <- auto_occ(
      ~ Forest* Year
      ~ 1,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.wind.8 <- auto_occ(
      ~ Fire + Year
      ~ 1,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.wind.9 <- auto_occ(
      ~ Fire * Year
      ~ 1,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

# Comparing models
p.wind.aic <- compare_models(
  list(null = p.win.d.null,
       Forest = p.wind.1,
       Fire = p.wind.2,
       Year = p.wind.3,
       `Forest+Fire` = p.wind.4,
       `Forest*Fire` = p.wind.5,
       `Forest+Year` = p.wind.6,
       `Forest*Year` =p.wind.7,
       `Fire+Year` = p.wind.8,
       `Fire*Year` = p.wind.9),
  digits = 2
)

p.wind.aic

write.csv(p.wind.aic, "Det_Deer_Fire_Winter.csv")

# Find best occupancy model
psi.wind.null <- auto_occ(
      ~ Forest* Fire
      ~1,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.wind.1 <- auto_occ(
      ~ Forest* Fire
      ~ Forest,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.wind.2 <- auto_occ(
      ~ Forest* Fire
      ~ Fire,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.wind.3 <- auto_occ(
      ~ Forest* Fire
      ~ Year,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



psi.wind.4 <- auto_occ(
      ~ Forest* Fire
      ~ Forest + Fire,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



psi.wind.5 <- auto_occ(
      ~ Forest* Fire
      ~ Forest * Fire,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.wind.6 <- auto_occ(
      ~ Forest* Fire
      ~ Forest + Year,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.wind.7 <- auto_occ(
      ~ Forest* Fire
      ~ Forest * Year,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.wind.8 <- auto_occ(
      ~ Forest* Fire
      ~ Fire + Year,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.wind.9 <- auto_occ(
      ~ Forest* Fire
      ~ Fire * Year,
      y= winter_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

# Comparing models
psi.wind..aic <- compare_models(
  list(null = psi.wind.null,
       Forest = psi.wind.1,
       Fire = psi.wind.2,
       Year = psi.wind.3,
       `Forest+Fire` = psi.wind.4,
       `Forest*Fire` = psi.wind.5,
       `Forest+Year` = psi.wind.6,
       `Forest*Year` =psi.wind.7,
       `Fire+Year` = psi.wind.8,
       `Fire*Year` = psi.wind.9),
  digits = 2
)

psi.wind..aic

pred.deer.win <- predict(psi.wind.7, type = "psi")

win_b <- summary(psi.wind.7)

dwin_b <- win_b@rho
owin_b <- win_b@psi

write.csv(dwin_b, "Det_Deer_Winter_Betas.csv")
write.csv(owin_b, "Occ_Deer_Winter_Betas.csv")


ggplot(data = pred.deer.win, aes(y= estimate, x= Year, colour = Forest))+
  geom_smooth()+
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.1, linetype = "dashed", fill = "white")+
  theme_classic()+
  ylab("Winter Deer Occupancy")+
  labs(color = "Forest Type")+
  scale_color_manual(values = c("A" = "#FFCC33", "M"= "red", "J"= "darkgreen"),label = c("Aspen Conifer", 
                            "Pinyon Juniper",
                            "Oak Maple"))+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text   = element_text(size=12, family = "serif", colour = "black"),
        legend.title  = element_text(size=12, family = "serif", colour = "black"),
        panel.border  = element_blank())+
  scale_y_continuous(limits = c(0, 1))


# Without legend

ggplot(data = pred.deer.win, aes(y= estimate, x= Year, colour = Forest))+
  geom_smooth()+
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.1, linetype = "dashed", fill = "white")+
  theme_classic()+
  ylab("Winter Deer Occupancy")+
  labs(color = "Forest Type")+
  scale_color_manual(values = c("A" = "#FFCC33", "M"= "red", "J"= "darkgreen"),label = c("Aspen Conifer", 
                            "Pinyon Juniper",
                            "Oak Maple"))+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text   = element_text(size=12, family = "serif", colour = "black"),
        legend.title  = element_text(size=12, family = "serif", colour = "black"),
        panel.border  = element_blank())+
  scale_y_continuous(limits = c(0, 1))+
  theme(legend.position = "none")

write.csv(psi.wind..aic, "Occ_Deer_Fire_Winter.csv")

```

# Fall only

```{r}

# Find best detection model

p.fall.d.null <- auto_occ(
      ~ 1
      ~1,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.fall.d.1 <- auto_occ(
      ~ Forest
      ~ 1,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.fall.d.2 <- auto_occ(
      ~ Fire
      ~ 1,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.fall.d.3 <- auto_occ(
      ~ Year
      ~ 1,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



p.fall.d.4 <- auto_occ(
      ~ Forest + Fire
      ~ 1,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



p.fall.d.5 <- auto_occ(
      ~ Forest* Fire
      ~ 1,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.fall.d.6 <- auto_occ(
      ~ Forest + Year
      ~ 1,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.fall.d.7 <- auto_occ(
      ~ Forest* Year
      ~ 1,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.fall.d.8 <- auto_occ(
      ~ Fire + Year
      ~ 1,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.fall.d.9 <- auto_occ(
      ~ Fire * Year
      ~ 1,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

# Comparing models
p.fall.d..aic <- compare_models(
  list(null = p.fall.d.null,
       Forest = p.fall.d.1,
       Fire = p.fall.d.2,
       Year = p.fall.d.3,
       `Forest+Fire` = p.fall.d.4,
       `Forest*Fire` = p.fall.d.5,
       `Forest+Year` = p.fall.d.6,
       `Forest*Year` =p.fall.d.7,
       `Fire+Year` = p.fall.d.8,
       `Fire*Year` = p.fall.d.9),
  digits = 2
)

p.fall.d..aic

write.csv(p.fall.d..aic, "Det_Deer_Fire_Fall.csv")

# Find best occupancy model
psi.fall.d.null <- auto_occ(
      ~ Forest* Fire
      ~1,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.fall.d.1 <- auto_occ(
      ~ Forest* Fire
      ~ Forest,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.fall.d.2 <- auto_occ(
      ~ Forest* Fire
      ~ Fire,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.fall.d.3 <- auto_occ(
      ~ Forest* Fire
      ~ Year,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



psi.fall.d.4 <- auto_occ(
      ~ Forest* Fire
      ~ Forest + Fire,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



psi.fall.d.5 <- auto_occ(
      ~ Forest* Fire
      ~ Forest * Fire,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.fall.d.6 <- auto_occ(
      ~ Forest* Fire
      ~ Forest + Year,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.fall.d.7 <- auto_occ(
      ~ Forest* Fire
      ~ Forest * Year,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.fall.d.8 <- auto_occ(
      ~ Forest* Fire
      ~ Fire + Year,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.fall.d.9 <- auto_occ(
      ~ Forest* Fire
      ~ Fire * Year,
      y= fall_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

# Comparing models
psi.fall.d..aic <- compare_models(
  list(null = psi.fall.d.null,
       Forest = psi.fall.d.1,
       Fire = psi.fall.d.2,
       Year = psi.fall.d.3,
       `Forest+Fire` = psi.fall.d.4,
       `Forest*Fire` = psi.fall.d.5,
       `Forest+Year` = psi.fall.d.6,
       `Forest*Year` =psi.fall.d.7,
       `Fire+Year` = psi.fall.d.8,
       `Fire*Year` = psi.fall.d.9),
  digits = 2
)

psi.fall.d..aic

# Best model 2

pred.deer.fall <- predict(psi.fall.d.2, type = "psi")

fall_b <- summary(psi.fall.d.2)

dfall_b <- fall_b@rho
ofall_b <- fall_b@psi

write.csv(dfall_b, "Det_Deer_Fall_Betas.csv")
write.csv(ofall_b, "Occ_Deer_Fall_Betas.csv")

ggplot(data = pred.deer.fall, aes(y = estimate, x = Fire)) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = lower, ymax = upper, width = 0.2)) +
  ylim(0, 1) +
  theme_classic() +
  ylab("Fall Deer Occupancy") +
  scale_x_discrete(labels = c("Unburned", "Burned")) +
  theme(
     text = element_text(family = "serif", size = 12, color = "black"),
    axis.title = element_text(size = 12, color = "black"),
    axis.text = element_text(size = 12, color = "black"),
    legend.text = element_text(size = 12, color = "black"),
    legend.title = element_text(size = 12, color = "black"),
    plot.title = element_text(size = 12, color = "black"),
    plot.subtitle = element_text(size = 12, color = "black"),
    plot.caption = element_text(size = 12, color = "black")
  )+
  theme(plot.margin = margin(10, 10, 10, 10))

write.csv(psi.fall.d..aic, "Occ_Deer_Fire_Fall.csv")

```

```{r}

# Find best detection model

p.spr.d.null <- auto_occ(
      ~ 1
      ~1,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.spr.d.1 <- auto_occ(
      ~ Forest
      ~ 1,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.spr.d.2 <- auto_occ(
      ~ Fire
      ~ 1,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.spr.d.3 <- auto_occ(
      ~ Year
      ~ 1,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



p.spr.d.4 <- auto_occ(
      ~ Forest + Fire
      ~ 1,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



p.spr.d.5 <- auto_occ(
      ~ Forest* Fire
      ~ 1,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.spr.d.6 <- auto_occ(
      ~ Forest + Year
      ~ 1,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.spr.d.7 <- auto_occ(
      ~ Forest* Year
      ~ 1,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.spr.d.8 <- auto_occ(
      ~ Fire + Year
      ~ 1,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

p.spr.d.9 <- auto_occ(
      ~ Fire * Year
      ~ 1,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

# Comparing models
p.spr.d..aic <- compare_models(
  list(null = p.spr.d.null,
       Forest = p.spr.d.1,
       Fire = p.spr.d.2,
       Year = p.spr.d.3,
       `Forest+Fire` = p.spr.d.4,
       `Forest*Fire` = p.spr.d.5,
       `Forest+Year` = p.spr.d.6,
       `Forest*Year` =p.spr.d.7,
       `Fire+Year` = p.spr.d.8,
       `Fire*Year` = p.spr.d.9),
  digits = 2
)

p.spr.d..aic

write.csv(p.spr.d..aic, "Det_Deer_Fire_Spring.csv")

# Find best occupancy model
psi.spr.d.null <- auto_occ(
      ~ Forest* Fire
      ~1,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.spr.d.1 <- auto_occ(
      ~ Forest* Fire
      ~ Forest,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.spr.d.2 <- auto_occ(
      ~ Forest* Fire
      ~ Fire,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.spr.d.3 <- auto_occ(
      ~ Forest* Fire
      ~ Year,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



psi.spr.d.4 <- auto_occ(
      ~ Forest* Fire
      ~ Forest + Fire,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)



psi.spr.d.5 <- auto_occ(
      ~ Forest* Fire
      ~ Forest * Fire,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.spr.d.6 <- auto_occ(
      ~ Forest* Fire
      ~ Forest + Year,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.spr.d.7 <- auto_occ(
      ~ Forest* Fire
      ~ Forest * Year,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.spr.d.8 <- auto_occ(
      ~ Forest* Fire
      ~ Fire + Year,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

psi.spr.d.9 <- auto_occ(
      ~ Forest* Fire
      ~ Fire * Year,
      y= spring_y,
      det_covs = Year_frame,
      occ_covs = Year_frame
)

# Comparing models
psi.spr.d..aic <- compare_models(
  list(null = psi.spr.d.null,
       Forest = psi.spr.d.1,
       Fire = psi.spr.d.2,
       Year = psi.spr.d.3,
       `Forest+Fire` = psi.spr.d.4,
       `Forest*Fire` = psi.spr.d.5,
       `Forest+Year` = psi.spr.d.6,
       `Forest*Year` =psi.spr.d.7,
       `Fire+Year` = psi.spr.d.8,
       `Fire*Year` = psi.spr.d.9),
  digits = 2
)

psi.spr.d..aic

pred.deer.spr <- predict(psi.spr.d.7, type = "psi")

spr_b <- summary(psi.spr.d.7)

dspr_b <- spr_b@rho
ospr_b <- spr_b@psi

write.csv(dspr_b, "Det_Deer_Spring_Betas.csv")
write.csv(ospr_b, "Occ_Deer_Spring_Betas.csv")

ggplot(data = pred.deer.spr, aes(y= estimate, x= Year, colour = Forest))+
  geom_smooth()+
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.1, linetype = "dashed", fill = "white")+
  theme_classic()+
  ylab("Spring Deer Occupancy")+
  labs(color = "Forest Type")+
  scale_color_manual(values = c("A" = "#FFCC33", "M"= "red", "J"= "darkgreen"),label = c("Aspen Conifer", 
                            "Pinyon Juniper",
                            "Oak Maple"))+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text   = element_text(size=12, family = "serif", colour = "black"),
        legend.title  = element_text(size=12, family = "serif", colour = "black"),
        panel.border  = element_blank())+
  scale_y_continuous(limits = c(0, 1))


# Without legend

ggplot(data = pred.deer.spr, aes(y= estimate, x= Year, colour = Forest))+
  geom_smooth()+
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.1, linetype = "dashed", fill = "white")+
  theme_classic()+
  ylab("Spring Deer Occupancy")+
  labs(color = "Forest Type")+
  scale_color_manual(values = c("A" = "#FFCC33", "M"= "red", "J"= "darkgreen"),label = c("Aspen Conifer", 
                            "Pinyon Juniper",
                            "Oak Maple"))+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text   = element_text(size=12, family = "serif", colour = "black"),
        legend.title  = element_text(size=12, family = "serif", colour = "black"),
        panel.border  = element_blank())+
  scale_y_continuous(limits = c(0, 1))+
  theme(legend.position = "none")

write.csv(psi.spr.d..aic, "Occ_Deer_Fire_Spring.csv")


```



