---
title: "Deer"
author: "R Pienaar"
date: "`r Sys.Date()`"
output: word_document
---

Occupancy and Relative Habitat Use for Mule Deer in the Pole Creek Megafire 
Burne area from 2019 to 2023 using camera trap data

Load packages 

```{r}


library(tidyverse)
library(camtrapR)
library(unmarked)
library(ggplot2)
library(MuMIn)

```

Input data
```{r}

rt = read.csv("C:/Users/ryanp/Documents/Dissertation/Chapter4_Camera traps/Camelot Exports/Record Tables/Record_table_mainpulated.csv")
head(rt)

ctt = read.csv("C:/Users/ryanp/Documents/Dissertation/Chapter4_Camera traps/Camelot Exports/Record Tables/Final_camtrap_table.csv")

#df <- df[c(1,4,6,7,8, 15,16)]

camop <- cameraOperation(CTtable = ctt,
                         stationCol = "Station",
                         sessionCol = "Session",
                         setupCol = "Setup_date",
                         retrievalCol = "Retrieval_date",
                         hasProblems = FALSE,             #The cameras were out the whole time, we don't know when the problems happened so I'm just keeping it as no problems
                         dateFormat = "mdy")



```

View data

```{r}

rt <- subset(rt, Species != "Unknown bird")      #remove birds and rabbits
rt <- subset(rt, Species != "Unknown lagomorph")

count_sp <- as.data.frame(table(rt$Species))  # show number of each species
count_sp
names(count_sp) <- c("Species", "N_Obs")

```


```{r}

sp_station <- table(rt$Species,rt$Station)
head(sp_station)

```


Detection History

```{r}

deerdh <- detectionHistory( recordTable = rt,
                            camOp = camop,
                            species = "Odocoileus hemionus",
                            stationCol = "Station",
                            speciesCol = "Species",
                            recordDateTimeCol = "Date",
                            recordDateTimeFormat = "mdy",
                            occasionLength = 30,
                            scaleEffort = FALSE,
                            timeZone = "MST",
                            day1 = "survey",
                            unmarkedMultFrameInput = TRUE)

#deerdh$detection_history

```

Occupancy analysis

```{r}


deeref <- deerdh$effort
deerdh <- deerdh$detection_history


Forest <- as.data.frame(substr(rownames(deerdh),5,5))
Fire <- as.data.frame(substr(rownames(deerdh),7,7))

covs <- cbind(Forest, Fire)
colnames(covs) <- c("Forest", "Fire")

deerocc <- unmarkedFrameOccu(y = deerdh, siteCovs = covs)

summary(deerocc)
#deerocc

```


Different site years occupancy analysis       

```{r}

year.sites <- ctt
year.sites$Station_Session <- paste(ctt$Station, ctt$Session +1, sep = "_")

for (i in year.sites) {
  year.sites$Session <- 1
}

ys.camop <- cameraOperation(CTtable = year.sites,
                            stationCol = "Station_Session",
                            sessionCol = "Session",
                            setupCol = "Setup_date",
                            retrievalCol = "Retrieval_date",
                            hasProblems = FALSE,
                            dateFormat = "mdy")

ys.rt <- rt

ys.rt$Station_Y <- paste(rt$Station, rt$YearsPostfire, sep = "_")

ys.rt <- subset(ys.rt, Species != "Unknown bird")      #remove birds and rabbits
ys.rt <- subset(ys.rt, Species != "Unknown lagomorph")

ys.count_sp <- as.data.frame(table(ys.rt$Species))  # show number of each species
ys.count_sp
names(ys.count_sp) <- c("Species", "N_Obs")

ys.sp_station <- table(ys.rt$Species, ys.rt$Station)
head(ys.sp_station)

ys.deerdh <- detectionHistory( recordTable = ys.rt,
                            camOp = ys.camop,
                            species = "Odocoileus hemionus",
                            stationCol = "Station_Y",
                            speciesCol = "Species",
                            recordDateTimeCol = "Date",
                            recordDateTimeFormat = "mdy",
                            occasionLength = 30,
                            scaleEffort = FALSE,
                            timeZone = "MST",
                            day1 = "survey",
                            unmarkedMultFrameInput = TRUE)

ys.deeref <- ys.deerdh$effort
ys.deerdh <- ys.deerdh$detection_history


ys.Forest <- as.data.frame(substr(rownames(ys.deerdh),5,5))
ys.Fire <- as.data.frame(substr(rownames(ys.deerdh),7,7))
Years_PostFire <- as.data.frame(substr(rownames(ys.deerdh),11,11))

ys.covs <- cbind(ys.Forest, ys.Fire, Years_PostFire)
colnames(ys.covs) <- c("Forest", "Fire", "Years_PostFire")

ys.deerocc <- unmarkedFrameOccu(y = ys.deerdh, siteCovs = ys.covs)
```

Detection model selection

```{r}

# Null deer model with constant detection and constant occupancy
do.d.1.1 <- occu(~1~1, data =  ys.deerocc)  #### detection first, then occupancy

###Constant occupancy
do.d.1.FoFiYf <- occu( ~ Forest + Fire  + Years_PostFire~1 , data = ys.deerocc)

do.d.1.FoFi <- occu( ~ Forest + Fire ~1 , data = ys.deerocc)
do.d.1.FoYf <- occu( ~ Forest + Years_PostFire ~1, data = ys.deerocc)
do.d.1.FiYF <- occu( ~ Fire + Years_PostFire ~1, data = ys.deerocc)

do.d.1.Yf <- occu( ~ Years_PostFire ~1, data = ys.deerocc)
do.d.1.Fo <- occu( ~ Forest ~1, data = ys.deerocc)
do.d.1.Fi <- occu( ~ Fire ~1, data = ys.deerocc)

### Interacting constant detection models
do.d.1.a <- occu( ~ Forest*Fire ~1, data = ys.deerocc)
do.d.1.b <- occu( ~ Forest*Years_PostFire ~1, data = ys.deerocc) 
do.d.1.c <- occu( ~ Fire*Years_PostFire ~1, data = ys.deerocc) 

do.d.list <- fitList(do.d.1.1, do.d.1.FoFiYf, do.d.1.FoFi, do.d.1.FoYf, do.d.1.FiYF,
                     do.d.1.Fi, do.d.1.Fo, do.d.1.Yf, do.d.1.a, do.d.1.b, do.d.1.c)

do.d.mod <- model.sel(do.d.1.1, do.d.1.FoFiYf, do.d.1.FoFi, do.d.1.FoYf, do.d.1.FiYF,
                     do.d.1.Fi, do.d.1.Fo, do.d.1.Yf, do.d.1.a, do.d.1.b, do.d.1.c)

modSel(do.d.list)
head(do.d.mod)
typeof(do.d.mod)
#write.csv(as.data.frame(do.d.mod), "deer_const_occ.csv")
## Best model is Forest, Fire and years postfire according to model.sel and modSel

```

Occupancy model selection

```{r}

# Null deer model with constant detection and constant occupancy
oo.d.1.1 <- occu(~1~1, data =  ys.deerocc)  #### detection first, then occupancy

### Occupancy with best detection model
oo.d.FoFiYf.FoFiYf <- occu(~Forest +Fire+ Years_PostFire ~ Forest + Fire + Years_PostFire , data = ys.deerocc)

oo.d.FoFiYf.FoFi <- occu(~Forest + Fire + Years_PostFire ~ Forest + Fire , data = ys.deerocc)
oo.d.FoFiYf.FoYf <- occu(~ Forest + Fire + Years_PostFire ~ Forest + Years_PostFire, data = ys.deerocc)
oo.d.FoFiYf.FiYF <- occu(~ Forest + Years_PostFire ~ Fire + Years_PostFire, data = ys.deerocc)

oo.d.FoFiYf.Yf <- occu(~ Forest + Fire + Years_PostFire ~ Years_PostFire, data = ys.deerocc)
oo.d.FoFiYf.Fo <- occu(~ Forest + Fire + Years_PostFire ~ Forest, data = ys.deerocc)
oo.d.FoFiYf.Fi <- occu(~ Forest + Fire + Years_PostFire ~ Fire, data = ys.deerocc)


oo.d.FoFiYf.a <- occu(~ Forest + Fire + Years_PostFire ~ Forest*Fire, data = ys.deerocc)
oo.d.FoFiYf.b <- occu(~ Forest + Fire + Years_PostFire ~ Forest*Years_PostFire, data = ys.deerocc) 
oo.d.FoFiYf.c <- occu(~ Forest + Fire + Years_PostFire ~ Fire*Years_PostFire, data = ys.deerocc) 

oo.d.list <- list(oo.d.1.1, oo.d.FoFiYf.FoFiYf, oo.d.FoFiYf.FoFi, oo.d.FoFiYf.FoYf, oo.d.FoFiYf.FiYF,
                     oo.d.FoFiYf.Fi, oo.d.FoFiYf.Fo, oo.d.FoFiYf.Yf, oo.d.FoFiYf.a, oo.d.FoFiYf.b, oo.d.FoFiYf.c)

oo.d.mod <- model.sel(oo.d.list)
oo.d.mod
oo.deer.avg <- get.models(oo.d.mod, subset = delta <= 4)

occ.deer.avg <- model.avg(oo.deer.avg)
head(oo.deer.avg)

#write.csv(as.data.frame(oo.d.mod), "deer_occ.csv")


```

Occupancy model outputs

```{r}

pred.data <- expand.grid(Forest = levels(ys.deerocc@siteCovs$Forest), 
                       Fire = levels(ys.deerocc@siteCovs$Fire),
                       Years_PostFire = levels(ys.deerocc@siteCovs$Years_PostFire))

coef(oo.deer.avg) %>%
  enframe

occ.deer.pred <- predict(occ.deer.avg, type = "state", newdata= pred.data, append = TRUE)

occ.deer.pred <- cbind(pred.data, occ.deer.pred)
occ.deer.pred

occ.deer.pred |> group_by(Years_PostFire) |>
  summarise(pred = mean(fit))


ggplot(data = occ.deer.pred, aes(Years_PostFire, fit))+
  geom_boxplot(fill = "grey")+
  theme_classic()

ggplot(data = occ.deer.pred, aes(Forest, fit))+
  geom_boxplot(fill = "grey")+
  theme_classic()

ggplot(data = occ.deer.pred, aes(Fire, fit))+
  geom_boxplot(fill = "grey")+
  theme_classic()

ggplot(data = occ.deer.pred, aes(Forest, fit, fill = Fire))+
  geom_boxplot()+
  theme_classic()

occ.deer.pred |> group_by(Forest, Fire,  fit) |>
  summarise(mean_fit = mean(fit),
            se_fit = sqrt(sum(se.fit^2)) / n()) |> 
  ggplot(aes(Forest, mean_fit, fill = Fire, color = Fire))+
  geom_boxplot()+
  geom_errorbar(aes(ymin = mean_fit-se_fit, ymax = mean_fit+se_fit),
                width = 0.3, position = position_dodge(0.75))+
  theme_classic()


```

Royle Nichols Relative Habitat Use
Detection

```{r}

# Null deer model with constant detection and constant occupancy
drn.d.1.1 <- occuRN(~1~1, data =  ys.deerocc)  #### detection first, then occuRNpancy

###Constant detection
drn.d.1.FoFiYf <- occuRN( ~ Forest + Fire + Years_PostFire ~ 1 , data = ys.deerocc)

drn.d.1.FoFi <- occuRN( ~ Forest + Fire ~1, data = ys.deerocc)
drn.d.1.FoYf <- occuRN( ~ Forest + Years_PostFire ~1, data = ys.deerocc)
drn.d.1.FiYF <- occuRN( ~ Fire + Years_PostFire ~1, data = ys.deerocc)

drn.d.1.Yf <- occuRN( ~ Years_PostFire ~1, data = ys.deerocc)
drn.d.1.Fo <- occuRN( ~ Forest ~1, data = ys.deerocc)
drn.d.1.Fi <- occuRN( ~ Fire ~1, data = ys.deerocc)

### Interacting constant detection models
drn.d.1.a <- occuRN( ~ Forest*Fire ~1, data = ys.deerocc)
drn.d.1.b <- occuRN( ~ Forest*Years_PostFire ~1, data = ys.deerocc) 
drn.d.1.c <- occuRN( ~ Fire*Years_PostFire ~1, data = ys.deerocc) 

drn.d.list <- fitList(drn.d.1.1, drn.d.1.FoFiYf, drn.d.1.FoFi, drn.d.1.FoYf, drn.d.1.FiYF,
                     drn.d.1.Fi, drn.d.1.Fo, drn.d.1.Yf, drn.d.1.a, drn.d.1.b, drn.d.1.c)

drn.d.mod <- model.sel(drn.d.1.1, drn.d.1.FoFiYf, drn.d.1.FoFi, drn.d.1.FoYf, drn.d.1.FiYF,
                     drn.d.1.Fi, drn.d.1.Fo, drn.d.1.Yf, drn.d.1.a, drn.d.1.b, drn.d.1.c)
drn.d.mod

#write.csv(as.data.frame(drn.d.mod),"deer_const_rn.csv")

## Best model is Forest interacting with fire

```

Relative habitat use with best detection model

```{r}

# Null deer model with constant detection and constant occupancy
orn.d.1.1 <- occuRN(~1~1, data =  ys.deerocc)  #### detection first, then occupancy

### Occupancy with best detection model
orn.d.FoFi.FoFiYf <- occuRN(~Forest * Fire ~ Forest + Fire + Years_PostFire , data = ys.deerocc)

orn.d.FoFi.FoFi <- occuRN(~Forest * Fire ~ Forest + Fire , data = ys.deerocc)
orn.d.FoFi.FoYf <- occuRN(~ Forest * Fire ~ Forest + Years_PostFire, data = ys.deerocc)
orn.d.FoFi.FiYF <- occuRN(~ Forest * Fire ~ Fire + Years_PostFire, data = ys.deerocc)

orn.d.FoFi.Yf <- occuRN(~ Forest * Fire ~ Years_PostFire, data = ys.deerocc)
orn.d.FoFi.Fo <- occuRN(~ Forest * Fire ~ Forest, data = ys.deerocc)
orn.d.FoFi.Fi <- occuRN(~ Forest * Fire ~ Fire, data = ys.deerocc)


orn.d.FoFi.a <- occuRN(~ Forest * Fire ~ Forest*Fire, data = ys.deerocc)
orn.d.FoFi.b <- occuRN(~ Forest * Fire ~ Forest*Years_PostFire, data = ys.deerocc) 
orn.d.FoFi.c <- occuRN(~ Forest * Fire ~ Fire*Years_PostFire, data = ys.deerocc) 

orn.d.mod <- model.sel(orn.d.1.1, orn.d.FoFi.FoFiYf, orn.d.FoFi.FoFi, orn.d.FoFi.FoYf, orn.d.FoFi.FiYF,
                     orn.d.FoFi.Fi, orn.d.FoFi.Fo, orn.d.FoFi.Yf, orn.d.FoFi.a, orn.d.FoFi.b, orn.d.FoFi.c)
head(orn.d.mod) # Average top models because they have uninformative parameters

#write.csv(as.data.frame(orn.d.mod), "deer_rn.csv")

rn.deer.avg <- get.models(orn.d.mod, subset = delta <= 4)

rn.deer.avg <- model.avg(rn.deer.avg)
head(rn.deer.avg)

```

Relative habitat use model outputs

```{r}

coef(rn.deer.avg) %>%
  enframe

rn.deer.pred <- predict(rn.deer.avg, type = "state", newdata = pred.data, append= TRUE)

rn.deer.pred <- cbind(pred.data, rn.deer.pred)
rn.deer.pred

rn.deer.pred |> group_by(Forest , Fire) |>
  summarise(pred = mean(fit))


ggplot(data = rn.deer.pred, aes(Years_PostFire, fit))+
  geom_boxplot(fill = "grey")+
  theme_classic()

ggplot(data = rn.deer.pred, aes(Forest, fit))+
  geom_boxplot(fill = "grey")+
  theme_classic()

ggplot(data = rn.deer.pred, aes(Fire, fit))+
  geom_boxplot(fill = "grey")+
  theme_classic()

ggplot(data = rn.deer.pred, aes(Forest, fit, fill = Fire))+
  geom_boxplot()+
  theme_classic()

rn.deer.pred |> group_by(Forest, Fire) |>
  summarise(mean_fit = mean(fit),
            se_fit = sqrt(sum(se.fit^2)) / n()) |>
  ggplot(aes(Forest, mean_fit, fill = Fire, color = Fire))+
  geom_boxplot()+
  geom_errorbar(aes(ymin = mean_fit-se_fit, ymax = mean_fit+se_fit),
                width = 0.3, position = position_dodge(0.75))+
  theme_classic()


```
