---
title: "Dynamic_occ_mod"
author: "R Pienaar"
date: "`r Sys.Date()`"
output: word_document
---

```{r}

library(unmarked)
library(camtrapR)
library(ggplot2)
library(tidyverse)
library(AICcmodavg)


```
Load data
```{r}

windowsFonts(A = windowsFont("Times New Roman"))

ct <- read.csv("C:/Users/ryanp/Documents/Dissertation/Chapter4_Camera traps/Camelot Exports/Record Tables/ct_summary.csv")
head(ct)

data <- read.csv("C:/Users/ryanp/Documents/Dissertation/Chapter4_Camera traps/Camelot Exports/Record Tables/Record_table_mainpulated.csv")
head(data)

```

create a detection history
```{r}
camop <- cameraOperation(CTtable      = ct,
                                    stationCol   = "Station",
                                    sessionCol = "Session",
                                    setupCol     = "Setup_date",
                                    retrievalCol = "Retrieval_date",
                                    hasProblems  = FALSE,
                                    dateFormat   = "mdy")

# without trapping effort
DetHist1 <- detectionHistory(recordTable         = data,
                            camOp                = camop,
                           species = "Odocoileus hemionus",
                            stationCol = "Station",
                            speciesCol = "Species",
                            recordDateTimeCol = "Date",
                            recordDateTimeFormat = "mdy",
                            occasionLength = 14,
                            scaleEffort = FALSE,
                            timeZone = "MST",
                            day1 = "survey",
                            unmarkedMultFrameInput = TRUE)

deerdh<- DetHist1$detection_history       


```

Create covariate data

```{r}

effort <- DetHist1$effort
head(effort)

YPF <- effort

YPF[,1:25] <- 2
YPF[,26:50] <- 3
YPF[,51:75] <- 4
YPF[,76:100] <- 5

obs_cov <- list(effort = effort,
                YPF = YPF)

YSC <- list(YPF=YPF)
  
Forest <- as.data.frame(substr(rownames(deerdh),5,5))
Fire <- as.data.frame(substr(rownames(deerdh),7,7))

site_cov <-  cbind(Forest, Fire)
colnames(site_cov) <- c("Forest", "Fire")
site_cov$Fire <- as.factor(site_cov$Fire)
site_cov$Forest <- as.factor(site_cov$Forest)

```

Create unmarked frame

```{r}
mat <- matrix(c(rep(2, 32), rep(3, 32), rep(4, 32), rep(5, 32)), nrow = 32, byrow = FALSE)
YSC <- list(years=mat)
deer_umf <- unmarkedMultFrame(y= deerdh,
                              obsCovs = obs_cov,
                              siteCovs = site_cov,
                              yearlySiteCovs = YSC,
                              numPrimary = 4)

summary(deer_umf)

```


Run Some Models!

First find optimal detection model
```{r}


### Null everything model
deer.dy.occ.null <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~1, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~1, # Detection
                           data = deer_umf)  

### Different detection models

#Iterative forward stepwise selection

deer.dy.occ.1 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~1, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ effort, # Detection
                           data = deer_umf) 

deer.dy.occ.2 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~1, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Fire, # Detection
                           data = deer_umf)  

deer.dy.occ.3 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~1, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest, # Detection
                           data = deer_umf)  

deer.dy.occ.4 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~1, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ years, # Detection
                           data = deer_umf)  

deer.dy.occ.5 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~1, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire, # Detection
                           data = deer_umf) 

deer.dy.occ.6 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~1, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire * years, # Detection
                           data = deer_umf) 

deer.dy.occ.7 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~1, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf) 





### Stepwise regression ####
mod.sel <- modSel(fitList(deer.dy.occ.null, deer.dy.occ.1, deer.dy.occ.2, deer.dy.occ.3, deer.dy.occ.4, deer.dy.occ.6, deer.dy.occ.7))
mod.sel

summary(deer.dy.occ.7)

### Best detection model = deer.dy.occ.7 (Fire * Forest * years + effort)

```

Best occupancy model

```{r}

#NUll Occupancy model is best model form colonization
deer.occ.null <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~1, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf) 

#### Forward iterative stepwise selection
deer.occ.1 <- colext(psiformula = ~ Forest, # Occupancy,
                           gammaformula = ~1, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf) 

deer.occ.2 <- colext(psiformula = ~ Fire, # Occupancy,
                           gammaformula = ~1, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf) 



deer.occ.3 <- colext(psiformula = ~ Forest * Fire, # Occupancy,
                           gammaformula = ~1, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf)  




# Model Selection
deer.occ.sel <- modSel(fitList(deer.occ.null, deer.occ.1, deer.occ.2, deer.occ.3))
deer.occ.sel
#Best model deer.occ.null (1)

```

Find best colonization model

```{r}

#### NUll colonization model is best extinction model
deer.col.null <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~1, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf)

### Setpwise forward iterative selection for colonization
deer.col.1 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~ years, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf)

deer.col.2 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~ Forest, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf)

deer.col.3 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~ Fire, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf)

deer.col.4 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~ Forest * Fire, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf)

deer.col.5 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~Forest * Fire * years, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf)

deer.col.6 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~ years + Forest, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf)

deer.col.7 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~ years + Fire, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf)


deer.col.8 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~ years + Forest * Fire, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf)



deer.col.sel <- modSel(fitList(deer.col.null, deer.col.1, deer.col.2, deer.col.3, deer.col.4, deer.col.5, 
                               deer.col.6, deer.col.7, deer.col.8))
deer.col.sel

#Best model deer.col.8 ((years+Forest*years))

```

Get best extinction model

```{r}

#Null model for extinciton (is the optimal model from detection)
deer.ext.null <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~ years + Forest * Fire, # Colonization
                           epsilonformula = ~1, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf)

#### Forward stepwise iterative selection for extinction
deer.ext.1 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~ years + Forest * Fire, # Colonization
                           epsilonformula = ~ years, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf) 

deer.ext.2 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~ years + Forest * Fire, # Colonization
                           epsilonformula = ~ Forest, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf) 

deer.ext.3 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~ years + Forest * Fire, # Colonization
                           epsilonformula = ~Fire, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf)

deer.ext.4 <- colext(psiformula = ~1,  # Occupancy,
                           gammaformula = ~ years + Forest * Fire, # Colonization
                           epsilonformula = ~ Forest*Fire, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf)

deer.ext.5 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~ years + Forest * Fire, # Colonization
                           epsilonformula = ~ Forest*Fire*years, # Extinction
                           pformula = ~ Forest * Fire * years + effort, # Detection
                           data = deer_umf) 

deer.ext.6 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~ years + Forest * Fire, # Colonization
                           epsilonformula = ~ Forest + years, # Extinction
                           pformula = ~  Forest * Fire * years + effort , # Detection
                           data = deer_umf) 

deer.ext.7 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~years + Forest * Fire, # Colonization
                           epsilonformula = ~ Forest + Fire, # Extinction
                           pformula = ~ Forest * Fire * years + effort , # Detection
                           data = deer_umf) 

deer.ext.8 <- colext(psiformula = ~1, # Occupancy,
                           gammaformula = ~years + Forest * Fire, # Colonization
                           epsilonformula = ~ Forest + Fire + years, # Extinction
                           pformula = ~ Forest * Fire * years + effort , # Detection
                           data = deer_umf) 

### Model Selection
deer.ext.sel <- modSel(fitList(deer.ext.null, deer.ext.1,deer.ext.2, deer.ext.3, deer.ext.4, 
                               deer.ext.5, deer.ext.6, deer.ext.7, deer.ext.8))
deer.ext.sel

### Best model is deer.ext.2 (Forest)



```




Final Model

```{r}

#### Check the AIC values for colonization and extinction to average across both


deer.avg <- deer.ext.2

deer.psi <- predict(deer.avg, type = "psi")
deer.ext <- predict(deer.avg, type = "ext")
deer.col <- predict(deer.avg, type = "col")
deer.det <- predict(deer.avg, type = "det")
sites <- rownames(DetHist1$detection_history)
row.names(deer.psi) <- sites

deer.psi <- data.frame(deer.psi)

deer.psi$site <- sites
deer.psi$forest <- substr(deer.psi$site,5,5)
deer.psi$fire <- substr(deer.psi$site,7,7)

summary(deer.avg)

```


Occupancy graph

```{r}



ggplot(data = deer.psi, aes(y = Predicted, x= forest))+
  geom_col(position = "dodge")+
  geom_errorbar(aes(ymin = lower, ymax = upper),
                width = 0.3, position = position_dodge(0.85))+
  ylab("Predicted Occupancy")+
  xlab(element_blank())+
  scale_x_discrete(labels = c("Aspen Conifer", "Pinyon Juniper", "Oak Maple"))+
  theme_classic()+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1))+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif", colour = "black"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text = element_text(size=12, family = "serif", colour = "black"),
        legend.title = element_text(size=12, family = "serif", colour = "black"),
        panel.border = element_blank())


```

Colonization graph

```{r}

head(deer.col)


#### Create data labels

site.years <-  rep(sites, each = 4)

site.years <- data.frame(Site = site.years, YPF = rep(2:5, length.out = length(site.years)))

deer.col <- cbind(deer.col, site.years)
deer.col$forest <- substr(deer.col$Site,5,5)
deer.col$fire <- substr(deer.col$Site,7,7)

ggplot(data = deer.col[deer.col$YPF!=5,], aes(y = Predicted, x = YPF, fill =  forest))+
  geom_col(position = "dodge")+
  geom_errorbar(aes(ymin = Predicted-SE, ymax = Predicted + SE),
                width = 0.3, position = position_dodge(0.85))+
  theme_classic()+
  ylab("Predicted Colonization")+
  xlab("Years Since Fire")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA))+
  guides(fill = guide_legend(title = "Forest Type"))+
  scale_fill_hue(labels = c("Aspen Conifer", "Pinyon Juniper", "Oak Maple"))+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif", colour = "black"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text = element_text(size=12, family = "serif", colour = "black"),
        legend.title = element_text(size=12, family = "serif", colour = "black"),
        panel.border = element_blank())


```

Create extinction graphs

```{r}

head(deer.ext)

deer.ext <- cbind(deer.ext, site.years) 
deer.ext$forest <- substr(deer.ext$Site,5,5)
deer.ext$fire <- substr(deer.ext$Site,7,7)

deer.ext[deer.ext$YPF!=5,] |> group_by(fire , forest)|>
  summarise(Predicted = mean(Predicted), SE = mean(SE)) |>
  ggplot( aes(x = fire, y = Predicted, fill = forest))+
   geom_col(position = "dodge")+
  geom_errorbar(aes(ymin = Predicted- SE, ymax = Predicted +SE),
                width = 0.3, position = position_dodge(0.85))+
  theme_classic() +
  ylab("Predicted Extinction")+
  xlab(element_blank())+
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA))+
  scale_x_discrete(labels = c("Unburned", "Burned"))+
  guides(fill = guide_legend(title = "Forest Type"))+
  scale_fill_hue(labels = c("Aspen Conifer", "Pinyon Juniper", "Oak Maple"))+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text = element_text(size=12, family = "serif", colour = "black"),
        legend.title = element_text(size=12, family = "serif", colour = "black"),
        panel.border = element_blank())




```

Output tables Deer
Model Selection Tables

```{r}
#Detection
mod.sel
mod.sel@Full[,c(1,2,38:44)]
write.csv(mod.sel@Full[,c(1,2,38:44)], "deer.det.sel.csv")

#Occupancy
deer.occ.sel
deer.occ.sel@Full[,c(1,2,48:54)]
write.csv(deer.occ.sel@Full[,c(1,2,48:54)], "deer.occ.sel.csv")

#Colonization
deer.col.sel
deer.col.sel@Full[, c(1,2,60:66)]
write.csv(deer.col.sel@Full[, c(1,2,60:66)], "deer.col.sel.csv")

#Extinction
deer.ext.sel
deer.ext.sel@Full[, c(1,2,72:78)]
write.csv(deer.ext.sel@Full[, c(1,2,72:78)], "deer.ext.sel.csv")





```
Coefficients plot

```{r}

nd1 <- data.frame(Forest= "A", Fire=as.factor(1), years=c(2:5), effort=14)
nd2 <- data.frame(Forest= "A", Fire=as.factor(0), years=c(2:5), effort=14)
nd3 <- data.frame(Forest= "J", Fire=as.factor(1), years=c(2:5), effort=14)
nd4 <- data.frame(Forest= "J", Fire=as.factor(0), years=c(2:5), effort=14)
nd5 <- data.frame(Forest= "M", Fire=as.factor(1), years=c(2:5), effort=14)
nd6 <- data.frame(Forest= "M", Fire=as.factor(0), years=c(2:5), effort=14)

nd <- rbind(nd1,nd2,nd3,nd4,nd5,nd6)
nd
det.pred <- predict(deer.ext.2, type = "det", newdata = nd)
det.pred <- cbind(nd,det.pred)

det.pred


ggplot(data = det.pred, aes(x= years, y =Predicted, colour = Forest))+
  geom_smooth(aes(fill =Forest))+
  theme_classic()

ggplot(data = det.pred, aes(x= years, y =Predicted, colour = Fire))+
  geom_smooth(aes(fill = Fire))+
  theme_classic()

```
Colonization Prediction

```{r}

col.pred <- predict(deer.ext.2, type = "col", newdata = nd)
col.pred <- cbind(nd, col.pred)
col.pred



ggplot(col.pred, aes(x = years, y = Predicted, color = Forest, shape = Fire, group = interaction(Forest, Fire))) +
  geom_point(position = position_dodge(width = 0.2), size = 3) +  # Adjust position of points
  geom_errorbar(aes(ymin = Predicted - SE, ymax = Predicted + SE), width = 0.2, position = position_dodge(width = 0.2)) +  # Add error bars
  geom_smooth(aes(group = interaction(Forest, Fire)), position = position_dodge(width = 0.2)) +  # Add trendlines
  theme_classic()+
  ylab("Colonization") +
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text   = element_text(size=12, family = "serif", colour = "black"),
        legend.title  = element_text(size=12, family = "serif", colour = "black"),
        panel.border  = element_blank())


ggplot(col.pred, aes(x = years, y = Predicted, color = Forest, shape = Fire, group = interaction(Forest, Fire))) +
  geom_point(position = position_dodge(width = 0.2), size = 3) +  # Adjust position of points
  geom_errorbar(aes(ymin = pmax(Predicted - SE, 0), ymax = pmin(Predicted + SE, 1)), width = 0.2, position = position_dodge(width = 0.2)) +  # Add error bars limited to [0, 1]
  geom_line(aes(group = interaction(Forest, Fire)), position = position_dodge(width = 0.2)) +  # Add trendlines
  ylim(0, 1) +  # Set y-axis limits
  theme_classic()

```

Extinction graph

```{r}

ext.pred <- predict(deer.ext.2, type = "ext", newdata = nd)
ext.pred <- cbind(nd, ext.pred)
ext.pred

ggplot(data = ext.pred, aes(x= Forest, y =Predicted, colour = Forest))+
  geom_point(size = 3)+
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2)+
  theme_classic()+
  ylab("Extinction")+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text   = element_text(size=12, family = "serif", colour = "black"),
        legend.title  = element_text(size=12, family = "serif", colour = "black"),
        panel.border  = element_blank())

```


Model fit evaluation

```{r}


gf.best <- parboot(deer.ext.2, nsim = 100)
gf.best
plot(gf.best)

```

