---
title: "Elk_burn"
author: "R Pienaar"
date: "`r Sys.Date()`"
output: html_document
---



Libraries

```{r}
# Load in libraries
library(camtrapR)
library(dplyr)
library(ggplot2)
library(devtools)
library(unmarked)
# Install autoOcc incase you have not yet
# devtools::install_github(
#   "mfidino/autoOcc",
#   build_vignettes = TRUE
# )
library(autoOcc)
```


```{r}


# Create a plots sub-folder as well to store figures
#  from analysis
dir.create("plots")
getwd()
# Set your local working directory and load in data that is stored
#  in autoOcc package.


#Load elk tables
ct <- read.csv("C:/Users/ryanp/Documents/Dissertation/Chapter4_Camera traps/Camelot Exports/Record Tables/ct_summary.csv")
head(ct)

data <- read.csv("C:/Users/ryanp/Documents/Dissertation/Chapter4_Camera traps/Camelot Exports/Record Tables/Record_table_mainpulated.csv")
head(data)

# Create a detection history for each season
camop <- cameraOperation(CTtable      = ct,
                                    stationCol   = "Station",
                                    sessionCol = "Session",
                                    setupCol     = "Setup_date",
                                    retrievalCol = "Retrieval_date",
                                    hasProblems  = FALSE,
                                    dateFormat   = "mdy")
# without trapping effort
DetHist1 <- detectionHistory(recordTable         = data,
                            camOp                = camop,
                           species = "Cervus elaphus",
                            stationCol = "Station",
                            speciesCol = "Species",
                            recordDateTimeCol = "Date",
                            recordDateTimeFormat = "mdy",
                            occasionLength = 14,
                            scaleEffort = FALSE,
                            timeZone = "MST",
                            day1 = "survey",
                            unmarkedMultFrameInput = TRUE)

elkdh <- DetHist1$detection_history
head(elkdh)
s1 <- elkdh[,1:25]
#s1$season <- 1
s2 <- elkdh[,26:50]
#s2$season <- 2
s3 <- elkdh[,51:75]
#s3$season <- 3
s4 <- elkdh[,76:100]
#s4$season <- 4

dh <- rbind(s1,s2,s3,s4)

sequence <- rep(1:4, each = 32)
dh <- as.data.frame(dh)
dh$season<- sequence
dh$site <- substr(row.names(dh),1,9)

#Create covariates for each site
elk_covariates <- as.data.frame(rownames(DetHist1$detection_history))
elk_covariates$Forest <- substr(elk_covariates$`rownames(DetHist1$detection_history)`,5,5)
elk_covariates$Fire <- substr(elk_covariates$`rownames(DetHist1$detection_history)`,7,7)

colnames(elk_covariates) <- c("Site", "Forest", "Fire")

# examine data
head(opossum_det_hist) 
head(dh)

#Create a season column in DH

length(rownames(dh))


```

```{r}


##elk
elk_y <- format_y(
  x = dh,
  site_column = "site",
  time_column = "season",
  history_columns = 1:25
)



```

Determine best detection model to be used to answer all questions

```{r}




# make named list (don't worry about the warning)
season_frame <- list(
   Season = matrix(
     dh$season,
     ncol = dim(elk_y)[2],
     nrow = dim(elk_y)[1]
   ),
   Forest = elk_covariates$Forest,
   Fire = elk_covariates$Fire
 )

# modeling with no covariates
pnull <- auto_occ(
  formula = ~1  # detection
            ~1, # occupancy
  y = elk_y
)



#### Iterative models
#### Original 3
p1 <- auto_occ(
      ~ Forest
      ~1,
      y= elk_y,
      det_covs = season_frame
)

p2 <- auto_occ(
      ~ Fire
      ~1,
      y= elk_y,
      det_covs = season_frame
)

p3 <- auto_occ(
      ~ Season
      ~1,
      y= elk_y,
      det_covs = season_frame
)

# Comparing models
detection.aic <- compare_models(
  list(null = pnull,
       Forest = p1,
       Fire = p2,
       Season = p3),
  digits = 2
)

detection.aic

#### First round best model is Forest
### Add season and fire with additiive and interactive effects to forest

p4 <- auto_occ(
      ~ Forest + Fire
      ~1,
      y= elk_y,
      det_covs = season_frame
)

p5 <- auto_occ(
      ~ Forest * Fire
      ~1,
      y= elk_y,
      det_covs = season_frame
)

p6 <- auto_occ(
      ~ Forest + Season
      ~1,
      y= elk_y,
      det_covs = season_frame
)

p7 <- auto_occ(
      ~ Forest * Season
      ~1,
      y= elk_y,
      det_covs = season_frame
)

detection.aic <- compare_models(
  list(null = pnull,
       Forest = p1,
       Fire = p2,
       Season = p3,
       `Forest+Fire` = p4,
       `Forest*Fire` = p5,
       `Forest+Season` = p6,
       `Forest*Season` =p7),
  digits = 2
)

efd<- detection.aic
#write.csv(efd, "Elk_Fire Detection.csv")
### Best model is model 7 Forest * Season acounting for 92% of the weight

```


Question 1
How does occupancy change in response to fire across forest types?

```{r}

q1 <- auto_occ(
  ~Forest * Season
  ~ Forest * Fire,
  y = elk_y,
  det_covs = season_frame,
  occ_covs = season_frame
)

summary(q1)



nd1 <- data.frame(Forest= "A", Fire=as.factor(1))
nd2 <- data.frame(Forest= "A", Fire=as.factor(0))
nd3 <- data.frame(Forest= "J", Fire=as.factor(1))
nd4 <- data.frame(Forest= "J", Fire=as.factor(0))
nd5 <- data.frame(Forest= "M", Fire=as.factor(1))
nd6 <- data.frame(Forest= "M", Fire=as.factor(0))

nd <- rbind(nd1,nd2,nd3,nd4,nd5,nd6)
nd

q1.predict <- predict(q1, type = "psi", newdata = nd)
q1.predict <- cbind(nd, q1.predict)
q1.predict


# Create the plot using the defined jitter position
ggplot(data = q1.predict, aes(x = Forest, y = estimate, colour = Fire)) +
  geom_point(size = 2, position = position_dodge(0.5)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, position = position_dodge(0.5)) +
  ylab("Elk Occupancy")+
  theme_classic()+
  theme(text = element_text(family = "serif", size = 12))+
  scale_x_discrete(label = c("Aspen Conifer", 
                             "Pinyon Juniper",
                             "Oak Maple"))+
  scale_color_discrete(labels = c("Burned", "Unburned"))+
  theme(
    text = element_text(family = "serif", size = 12),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 12),
    plot.subtitle = element_text(size = 12),
    plot.caption = element_text(size = 12)
  )+ylim(0,1)

```

Question 2
How does occupancy change in response to fire severity across forest types?


```{r}

#Create covariates for each site


sev.df <- read.csv("C:/Users/ryanp/Documents/Dissertation/Chapter4_Camera traps/Dynamic_Occ/Chapter-4/FireSeverity.csv")
sev.df <-sev.df[-c(27,28),]

sev.df <- sev.df %>% replace(is.na(.), 0)

elk_covariates$FireSev <- sev.df$Fire_severity
head(elk_covariates)

```

Best detection for Fire Severity

```{r}


# make named list (don't worry about the warning)
season_frame <- list(
   Season = matrix(
     dh$season,
     ncol = dim(elk_y)[2],
     nrow = dim(elk_y)[1]
   ),
   Forest = elk_covariates$Forest,
   FireSev = elk_covariates$FireSev
 )

# modeling with no covariates
pnull <- auto_occ(
  formula = ~1  # detection
            ~1, # occupancy
  y = elk_y
)


#### Iterative models
#### Original 3
p1 <- auto_occ(
      ~ Forest
      ~1,
      y= elk_y,
      det_covs = season_frame
)

p2 <- auto_occ(
      ~ FireSev
      ~1,
      y= elk_y,
      det_covs = season_frame
)

p3 <- auto_occ(
      ~ Season
      ~1,
      y= elk_y,
      det_covs = season_frame
)

# Comparing models
detection.aic <- compare_models(
  list(null = pnull,
       Forest = p1,
       FireSev = p2,
       Season = p3),
  digits = 2
)

detection.aic

#### First round best model is Forest
### Add season and fire with additiive and interactive effects to forest

p4 <- auto_occ(
      ~ Forest + FireSev
      ~1,
      y= elk_y,
      det_covs = season_frame
)

p5 <- auto_occ(
      ~ Forest * FireSev
      ~1,
      y= elk_y,
      det_covs = season_frame
)

p6 <- auto_occ(
      ~ Forest + Season
      ~1,
      y= elk_y,
      det_covs = season_frame
)

p7 <- auto_occ(
      ~ Forest * Season
      ~1,
      y= elk_y,
      det_covs = season_frame
)

# Comparing models
detection.aic <- compare_models(
  list(null = pnull,
       Forest = p1,
       FireSev = p2,
       Season = p3,
       `Forest+FireSev` = p4,
       `Forest*FireSev` = p5,
       `Forest+Season` = p6,
       `Forest*Season` =p7),
  digits = 2
)

efsd <- detection.aic
#write.csv(efsd, "Elk_FireSev_Detection.csv")
### Best model is model 7 Forest + FireSev acounting for 55% of the weight

```

Occupancy response to fire severity across fire types

```{r}


q2 <- auto_occ(
  ~Forest * FireSev
  ~ Forest * FireSev,
  y = elk_y,
  det_covs = season_frame,
  occ_covs = season_frame
)

summary(q2)

# nd1 <- data.frame(Forest= "A", Fire=as.factor(1), years=c(2:5), effort=14)
# nd2 <- data.frame(Forest= "A", Fire=as.factor(0), years=c(2:5), effort=14)
# nd3 <- data.frame(Forest= "J", Fire=as.factor(1), years=c(2:5), effort=14)
# nd4 <- data.frame(Forest= "J", Fire=as.factor(0), years=c(2:5), effort=14)
# nd5 <- data.frame(Forest= "M", Fire=as.factor(1), years=c(2:5), effort=14)
# nd6 <- data.frame(Forest= "M", Fire=as.factor(0), years=c(2:5), effort=14)
# 
# nd <- rbind(nd1,nd2,nd3,nd4,nd5,nd6)
# nd

nd1 <- data.frame(Forest= "A", FireSev = c(0:4))

nd3 <- data.frame(Forest= "J", FireSev= c(0:4))

nd5 <- data.frame(Forest= "M", FireSev = c(0:4))


nd <- rbind(nd1,nd3,nd5)
nd

q2.predict <- predict(q2, type = "psi", newdata = nd)
q2.predict <- cbind(nd, q2.predict)
q2.predict



# Create the plot using the defined jitter position
ggplot(data = q2.predict, aes(x = FireSev, y = estimate, colour = Forest)) +
  geom_point(size = 2, position = position_dodge(0.5)) +
  geom_line(position = position_dodge(0.5))+
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, position = position_dodge(0.5)) +
  theme_classic()+
  ylab("Elk Occupancy")+
  theme(text = element_text(family = "serif", size = 12))+
  scale_color_discrete(label = c("Aspen Conifer", 
                             "Pinyon Juniper",
                             "Oak Maple"))+
  theme(
    text = element_text(family = "serif", size = 12),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 12),
    plot.subtitle = element_text(size = 12),
    plot.caption = element_text(size = 12)
  )+ylim(0,1)


```


Question 3
How does occupancy vary across time in burned areas across forest types?
This is where model selection comes in 

Fitting models

```{r}



# make named list (don't worry about the warning)
season_frame <- list(
   Season = matrix(
     dh$season,
     ncol = dim(elk_y)[2],
     nrow = dim(elk_y)[1]
   ),
   Forest = elk_covariates$Forest,
   Fire = elk_covariates$Fire
 )


### Lets find the best occupancy model

# Find best occupancy model
psinull <- auto_occ(
      ~ Forest* Season
      ~1,
      y= elk_y,
      det_covs = season_frame,
      occ_covs = season_frame
)

psi1 <- auto_occ(
      ~ Forest* Season
      ~ Forest,
      y= elk_y,
      det_covs = season_frame,
      occ_covs = season_frame
)

psi2 <- auto_occ(
      ~ Forest* Season
      ~ Fire,
      y= elk_y,
      det_covs = season_frame,
      occ_covs = season_frame
)

psi3 <- auto_occ(
      ~ Forest* Season
      ~ Season,
      y= elk_y,
      det_covs = season_frame,
      occ_covs = season_frame
)

# Comparing models
psi.aic <- compare_models(
  list(null = psinull,
       Forest = psi1,
       Fire = psi2,
       Season = psi3),
  digits = 2
)

psi.aic

### Iterative selection round 2


psi4 <- auto_occ(
      ~ Forest* Season
      ~ Fire + Forest,
      y= elk_y,
      det_covs = season_frame,
      occ_covs = season_frame
)



psi5 <- auto_occ(
      ~ Forest* Season
      ~ Fire * Forest,
      y= elk_y,
      det_covs = season_frame,
      occ_covs = season_frame
)

psi6 <- auto_occ(
      ~ Forest* Season
      ~ Fire + Season,
      y= elk_y,
      det_covs = season_frame,
      occ_covs = season_frame
)

psi7 <- auto_occ(
      ~ Forest* Season
      ~ Fire * Season,
      y= elk_y,
      det_covs = season_frame,
      occ_covs = season_frame
)



# Comparing models
psi.aic <- compare_models(
  list(null = psinull,
       Forest = psi1,
       Fire = psi2,
       Season = psi3,
       `Fire+Forest` = psi4,
       `Fire*Forest` = psi5,
       `Fire+Season` = psi6,
       `Fire*Season` =psi7),
  digits = 2
)

psi.aic

variables <- list(
  Forest = c("Forest*Season", "Forest", "Forest+Fire", "Forest+Season", "Forest*Fire"),
  Season = c("Forest*Season", "Forest+Season", "Season"),
  Fire = c("Forest+Fire", "Fire", "Forest*Fire")
)

#### Lots of top competing models

#Calculate relative variable importance

importance<- sapply(variables, function(models){
  sum(psi.aic$AICwt[psi.aic$model %in% models])
})

importance <- as.data.frame(importance)
importance$variable <- row.names(importance)


ggplot(importance, aes(x = importance, y = variable)) +
  geom_point(size = 3, color = "blue") +
  geom_text(aes(label = importance), hjust = -0.2, size = 4) +
  labs(x = "Relative Importance (w+)", y = "Variable", 
       title = "Relative Variable Importance") +
  theme_classic() +
  xlim(0, 1)+
  theme(
    text = element_text(family = "serif", size = 12),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 12),
    plot.subtitle = element_text(size = 12),
    plot.caption = element_text(size = 12)
  )


```

Model Averaging

```{r}

# To model average, get the parameters in each model,
# and set up a binary matrix to denote if they were present or not in that model.

# create model list again
model_list <- list(a=psinull,b=psi1,c=psi2,d=psi3,e=psi4,f=psi5,g=psi6,h=psi7)

# and AIC results
aic_results <- compare_models(
  model_list
)

aic_results

# reorder the model_list based on relative fit
model_list <- model_list[aic_results$model]

model_list


aic_results$model
# specify confidence interval width
my_ci_width <- 0.95


# get only the model parameters 
parms <- lapply(
  model_list,
  function(x){
    x@estimates$parameter
  }
)


# select only unique parameters
all_parms <- unique(
  unlist(
    parms
  )
)

# make an empty matrix
parm_matrix <- matrix(
  0,
  ncol = length(
    all_parms
  ),
  nrow = length(
    model_list
  )
)
colnames(parm_matrix) <- all_parms

# Add '1's to models which have parameter present
for(i in 1:nrow(parm_matrix)){
  parm_matrix[i, parms[[i]]] <- 1
}

# calculate overall weight for each parameter. The easiest
#  way to do this is to make a weight matrix.
weight_matrix <- matrix(
  aic_results$AICwt,
  nrow = length(model_list),
  ncol = length(all_parms)
)

parm_weight <- colSums(
  parm_matrix * weight_matrix
)

parm_weight

#  We are going to take samples from the parameters (which
#  is the same thing we do to make predictions
#  via autoOcc::predict). To do that, we need
#  to get the variance covariance matrix
#  for each model.

cov_mat <- lapply(
  model_list,
  vcov
)

# and now the estimates (assuming you are not
# using any offsets in the model for this).

ests <- lapply(
  model_list,
  function(x) x@estimates$Est
)

# do 5000 samples for each parameter.
mvn_samps <- vector(
  "list",
  length = length(model_list)
)
nsim = 5000
set.seed(465)
for(i in 1:length(mvn_samps)){
  mvn_samps[[i]] <- mvtnorm::rmvnorm(
    nsim,
    mean = ests[[i]],
    sigma = cov_mat[[i]],
    method = "svd"
  )
  colnames(mvn_samps[[i]]) <- parms[[i]]
}

# do model averaging for each parameter
avg_parm <- data.frame(
  parameter = all_parms,
  est = NA,
  lower = NA,
  upper = NA
)

for(i in 1:nrow(avg_parm)){
  my_parm <- avg_parm$parameter[i]
  which_models <- which(
    parm_matrix[,i] == 1
  )
  
  weights <- weight_matrix[
    which_models,i
  ] * parm_matrix[
    which_models,i
  ]
  
  # get beta terms
  beta_mat <- matrix(
    NA,
    ncol = length(which_models),
    nrow = nsim
  )
  
  # multiply weight across columns while we do this
  for(j in 1:ncol(beta_mat)){
    beta_mat[,j] <- mvn_samps[[which_models[j]]][,my_parm] *
      weights[j]
  }
  
  # sum each row
  beta_mat <- rowSums(beta_mat)
  
  # divide by overall weight
  beta_mat <- beta_mat / parm_weight[i]
  
  # summarise
  avg_parm$est[i] <- median(beta_mat)
  avg_parm$lower[i] <- quantile(
    beta_mat,
    (1 - my_ci_width) / 2
  )
  avg_parm$upper[i] <- quantile(
    beta_mat,
    1 - ( (1 - my_ci_width) / 2 )
  )
  
}


# get average estimate
avg_parm %>% 
  mutate(
    across(
      where(is.numeric), ~ round(., digits = 2))
    )
  
avg_parm

data_filtered <- avg_parm %>%
  filter(!grepl("^rho", parameter))

ggplot(data= data_filtered, aes(x = est, y = parameter)) +
  geom_point() +
  geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.2) +
  labs(title = "Model averaging for Occupancy",
       x = "Estimate",
       y = "Parameter") +
  theme_classic()+
  theme(
    text = element_text(family = "serif", size = 12),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 12),
    plot.subtitle = element_text(size = 12),
    plot.caption = element_text(size = 12)
  )

```

Predict occupancy

```{r}


#### Plot best model

nd<-data.frame(Fire= c(1,0))
nd$Fire <- as.factor(nd$Fire)
nd

pred.top <- predict(psi2, type = "psi", newdata = nd)
pred.top <- cbind(nd, pred.top)

pred.top$Fire <- as.factor(pred.top$Fire)

ggplot(data = pred.top, aes(y = estimate, x = Fire)) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = lower, ymax = upper, width = 0.2)) +
  ylim(0, 1) +
  theme_classic() +
  ylab("Elk Occupancy") +
  scale_x_discrete(labels = c("Unburned", "Burned")) +
  theme(
    text = element_text(family = "serif", size = 12),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 12),
    plot.subtitle = element_text(size = 12),
    plot.caption = element_text(size = 12)
  )




```

Rerun model selection but with Fire Severity

Fitting models

```{r}



# make named list (don't worry about the warning)
season_frame <- list(
   Season = matrix(
     dh$season,
     ncol = dim(elk_y)[2],
     nrow = dim(elk_y)[1]
   ),
   Forest = elk_covariates$Forest,
   FireSev = elk_covariates$FireSev
 )


### Lets find the best occupancy model

# Find best occupancy model
psinull <- auto_occ(
      ~ Forest* Season
      ~1,
      y= elk_y,
      det_covs = season_frame,
      occ_covs = season_frame
)

psi1 <- auto_occ(
      ~ Forest* Season
      ~ Forest,
      y= elk_y,
      det_covs = season_frame,
      occ_covs = season_frame
)

psi2 <- auto_occ(
      ~ Forest* Season
      ~ FireSev,
      y= elk_y,
      det_covs = season_frame,
      occ_covs = season_frame
)

psi3 <- auto_occ(
      ~ Forest* Season
      ~ Season,
      y= elk_y,
      det_covs = season_frame,
      occ_covs = season_frame
)

# Comparing models
psi.aic <- compare_models(
  list(null = psinull,
       Forest = psi1,
       FireSev = psi2,
       Season = psi3),
  digits = 2
)

psi.aic

#Best model is null model

variables <- list(
  Forest = c("Forest*Season", "Forest", "Forest+FireSev", "Forest+Season", "Forest*FireSev"),
  Season = c("Forest*Season", "Forest+Season", "Season"),
  FireSev = c("Forest+FireSev", "FireSev", "Forest*FireSev")
)

#### Lots of top competing models

#Calculate relative variable importance

importance<- sapply(variables, function(models){
  sum(psi.aic$AICwt[psi.aic$model %in% models])
})

importance <- as.data.frame(importance)
importance$variable <- row.names(importance)


ggplot(importance, aes(x = importance, y = variable)) +
  geom_point(size = 3, color = "blue") +
  geom_text(aes(label = importance), hjust = -0.2, size = 4) +
  labs(x = "Relative Importance (w+)", y = "Variable", 
       title = "Relative Variable Importance") +
  theme_classic() +
  xlim(0, 1)+
  theme(
    text = element_text(family = "serif", size = 12),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 12),
    plot.subtitle = element_text(size = 12),
    plot.caption = element_text(size = 12)
  )


```

Model Averaging

```{r}

# To model average, get the parameters in each model,
# and set up a binary matrix to denote if they were present or not in that model.

# create model list again
model_list <- list(a=psinull,b=psi1,c=psi2,d=psi3)

# and AIC results
aic_results <- compare_models(
  model_list
)

aic_results

# reorder the model_list based on relative fit
model_list <- model_list[aic_results$model]

model_list


aic_results$model
# specify confidence interval width
my_ci_width <- 0.95


# get only the model parameters 
parms <- lapply(
  model_list,
  function(x){
    x@estimates$parameter
  }
)


# select only unique parameters
all_parms <- unique(
  unlist(
    parms
  )
)

# make an empty matrix
parm_matrix <- matrix(
  0,
  ncol = length(
    all_parms
  ),
  nrow = length(
    model_list
  )
)
colnames(parm_matrix) <- all_parms

# Add '1's to models which have parameter present
for(i in 1:nrow(parm_matrix)){
  parm_matrix[i, parms[[i]]] <- 1
}

# calculate overall weight for each parameter. The easiest
#  way to do this is to make a weight matrix.
weight_matrix <- matrix(
  aic_results$AICwt,
  nrow = length(model_list),
  ncol = length(all_parms)
)

parm_weight <- colSums(
  parm_matrix * weight_matrix
)

parm_weight

#  We are going to take samples from the parameters (which
#  is the same thing we do to make predictions
#  via autoOcc::predict). To do that, we need
#  to get the variance covariance matrix
#  for each model.

cov_mat <- lapply(
  model_list,
  vcov
)

# and now the estimates (assuming you are not
# using any offsets in the model for this).

ests <- lapply(
  model_list,
  function(x) x@estimates$Est
)

# do 5000 samples for each parameter.
mvn_samps <- vector(
  "list",
  length = length(model_list)
)
nsim = 5000
set.seed(465)
for(i in 1:length(mvn_samps)){
  mvn_samps[[i]] <- mvtnorm::rmvnorm(
    nsim,
    mean = ests[[i]],
    sigma = cov_mat[[i]],
    method = "svd"
  )
  colnames(mvn_samps[[i]]) <- parms[[i]]
}

# do model averaging for each parameter
avg_parm <- data.frame(
  parameter = all_parms,
  est = NA,
  lower = NA,
  upper = NA
)

for(i in 1:nrow(avg_parm)){
  my_parm <- avg_parm$parameter[i]
  which_models <- which(
    parm_matrix[,i] == 1
  )
  
  weights <- weight_matrix[
    which_models,i
  ] * parm_matrix[
    which_models,i
  ]
  
  # get beta terms
  beta_mat <- matrix(
    NA,
    ncol = length(which_models),
    nrow = nsim
  )
  
  # multiply weight across columns while we do this
  for(j in 1:ncol(beta_mat)){
    beta_mat[,j] <- mvn_samps[[which_models[j]]][,my_parm] *
      weights[j]
  }
  
  # sum each row
  beta_mat <- rowSums(beta_mat)
  
  # divide by overall weight
  beta_mat <- beta_mat / parm_weight[i]
  
  # summarise
  avg_parm$est[i] <- median(beta_mat)
  avg_parm$lower[i] <- quantile(
    beta_mat,
    (1 - my_ci_width) / 2
  )
  avg_parm$upper[i] <- quantile(
    beta_mat,
    1 - ( (1 - my_ci_width) / 2 )
  )
  
}


# get average estimate
avg_parm %>% 
  mutate(
    across(
      where(is.numeric), ~ round(., digits = 2))
    )
  
avg_parm

data_filtered <- avg_parm %>%
  filter(!grepl("^rho", parameter))

ggplot(data= data_filtered, aes(x = est, y = parameter)) +
  geom_point() +
  geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.2) +
  labs(title = "Model averaging for Occupancy",
       x = "Estimate",
       y = "Parameter") +
  theme_classic()+
  theme(
    text = element_text(family = "serif", size = 12),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.title = element_text(size = 12),
    plot.subtitle = element_text(size = 12),
    plot.caption = element_text(size = 12)
  )


```



Predict occupancy

```{r}


#### Plot best model



pred.top <- predict(psinull, type = "psi")

pred.top



ggplot(data = pred.top, aes(y =estimate, x=0))+
  geom_point()+
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2)+
  theme_classic()+
  ylab("Elk Occupancy")+
  theme(plot.title    = element_text(size=12, family = "serif", colour = "black"),
        plot.subtitle = element_text(size=12, family = "serif"),
        axis.title.x  = element_text(size=12, family = "serif", colour = "black"),
        axis.title.y  = element_text(size=12, family = "serif", colour = "black"),
        axis.text.x   = element_text(size=12, family = "serif", colour = "black"),
        axis.text.y   = element_text(size=12, family = "serif", colour = "black"),
        legend.text   = element_text(size=12, family = "serif", colour = "black"),
        legend.title  = element_text(size=12, family = "serif", colour = "black"),
        panel.border  = element_blank())+
  theme(
    axis.title.x = element_blank(),  # Remove x-axis title
    axis.text.x = element_blank(),   # Remove x-axis text
    axis.ticks.x = element_blank()   # Remove x-axis ticks
  )+
  scale_y_continuous(limits = c(0, 1)) +  # Set y-axis limits from 0 to 1
  scale_x_continuous(expand = c(0, 10), breaks = NULL)

```




