---
title: "Chapter 4"
author: "R Pienaar"
date: "`r Sys.Date()`"
output:
  word_document: default
  pdf_document: default
---

Load packages

```{r}


library(tidyverse)
library(camtrapR)
library(exiftoolr)
library(unmarked)
library(ggplot2)
library(MuMIn)


Sys.which("exiftool.exe") ### Where is exiftool?
exiftoolPath("C:/Users/ryanp/Documents/Dissertation/Raw data/Nebo Fire/Camera Base 1.7/Fixes/EXIFTool/exiftoolgui/exiftool.exe")

```



Input data
```{r}

rt = read.csv("C:/Users/ryanp/Documents/Dissertation/Chapter4_Camera traps/Camelot Exports/Record Tables/Record_table_mainpulated.csv")
head(rt)

ctt = read.csv("C:/Users/ryanp/Documents/Dissertation/Chapter4_Camera traps/Camelot Exports/Record Tables/Final_camtrap_table.csv")

#df <- df[c(1,4,6,7,8, 15,16)]

camop <- cameraOperation(CTtable = ctt,
                         stationCol = "Station",
                         sessionCol = "Session",
                         setupCol = "Setup_date",
                         retrievalCol = "Retrieval_date",
                         hasProblems = FALSE,             #The cameras were out the whole time, we don't know when the problems happened so I'm just keeping it as no problems
                         dateFormat = "mdy")



```


View data

```{r}

rt <- subset(rt, Species != "Unknown bird")      #remove birds and rabbits
rt <- subset(rt, Species != "Unknown lagomorph")

count_sp <- as.data.frame(table(rt$Species))  # show number of each species
count_sp
names(count_sp) <- c("Species", "N_Obs")

```

```{r}

sp_station <- table(rt$Species,rt$Station)
head(sp_station)


```



Detection History

```{r}

deerdh <- detectionHistory( recordTable = rt,
                            camOp = camop,
                            species = "Odocoileus hemionus",
                            stationCol = "Station",
                            speciesCol = "Species",
                            recordDateTimeCol = "Date",
                            recordDateTimeFormat = "mdy",
                            occasionLength = 30,
                            scaleEffort = FALSE,
                            timeZone = "MST",
                            day1 = "survey",
                            unmarkedMultFrameInput = TRUE)

#deerdh$detection_history

```

Occupancy analysis

```{r}

library(unmarked)
deeref <- deerdh$effort
deerdh <- deerdh$detection_history


Forest <- as.data.frame(substr(rownames(deerdh),5,5))
Fire <- as.data.frame(substr(rownames(deerdh),7,7))

covs <- cbind(Forest, Fire)
colnames(covs) <- c("Forest", "Fire")

deerocc <- unmarkedFrameOccu(y = deerdh, siteCovs = covs)

summary(deerocc)
#deerocc

```

Create Models (Single season)

```{r}



# Null deer model with constant detection and constant occupancy
d.1.1 <- occu(~1~1, data =  deerocc)  #### detection first, then occupancy
d.1.1

d.1.1.psi <- backTransform(d.1.1, type = "state") #Occupancy
d.1.1.psi

d.1.1.p <- backTransform(d.1.1, type = "det") #Detection
d.1.1.p

d.1.1.psi.ci <- confint(d.1.1.psi)
d.1.1.p.ci <- confint(d.1.1.p)

###Constant detection
d.1.FoFi <- occu(~1 ~ Forest + Fire, data = deerocc)
d.1.FoFi

d.1.Fo <- occu(~1 ~ Forest, data = deerocc)
d.1.Fi <- occu(~1 ~ Fire, data = deerocc)


#Constant occupancy
d.FoFi.1 <- occu(~Forest + Fire ~1, data = deerocc)
d.FoFi.1

d.Fo.1 <- occu(~ Forest ~1, data = deerocc)
d.Fi.1 <- occu(~ Fire ~1, data = deerocc)

# Full model
d.FoFi.FoFi <- occu(~Forest + Fire ~Forest+Fire, data = deerocc)

```

Model Selection with constant occupancy to evaluate detection

```{r}

d.const.occ <- fitList(d.FoFi.1,d.Fo.1, d.Fi.1, d.1.1)
modSel(d.const.occ)

d.FoFi.1
newdata <- expand.grid(Forest = levels(deerocc@siteCovs$Forest), 
                       Fire = levels(deerocc@siteCovs$Fire))

det.mod.pred <- predict(d.FoFi.1, type = "det", newdata = newdata, append = TRUE)
det.mod.pred

```

Full Model Selection

```{r}

d.full.occ <- fitList(d.FoFi.1,d.Fo.1, d.Fi.1, d.1.1, d.1.Fi,d.1.Fo, d.1.FoFi, d.FoFi.FoFi)
modSel(d.full.occ)

d.FoFi.1

full.mod.pred <- predict(d.FoFi.1, type = "det", newdata = newdata, append = TRUE)
full.mod.pred

```



Create models (multiseason)

```{r}

#deer1 <- colext(~1 ~1 ~1 ~1, data = deerocc)

```

Different site years occupancy analysis       

```{r}

year.sites <- ctt
year.sites$Station_Session <- paste(ctt$Station, ctt$Session +1, sep = "_")

for (i in year.sites) {
  year.sites$Session <- 1
}

ys.camop <- cameraOperation(CTtable = year.sites,
                            stationCol = "Station_Session",
                            sessionCol = "Session",
                            setupCol = "Setup_date",
                            retrievalCol = "Retrieval_date",
                            hasProblems = FALSE,
                            dateFormat = "mdy")

ys.rt <- rt

ys.rt$Station_Y <- paste(rt$Station, rt$YearsPostfire, sep = "_")

ys.rt <- subset(ys.rt, Species != "Unknown bird")      #remove birds and rabbits
ys.rt <- subset(ys.rt, Species != "Unknown lagomorph")

ys.count_sp <- as.data.frame(table(ys.rt$Species))  # show number of each species
ys.count_sp
names(ys.count_sp) <- c("Species", "N_Obs")

ys.sp_station <- table(ys.rt$Species, ys.rt$Station)
head(ys.sp_station)

ys.deerdh <- detectionHistory( recordTable = ys.rt,
                            camOp = ys.camop,
                            species = "Odocoileus hemionus",
                            stationCol = "Station_Y",
                            speciesCol = "Species",
                            recordDateTimeCol = "Date",
                            recordDateTimeFormat = "mdy",
                            occasionLength = 30,
                            scaleEffort = FALSE,
                            timeZone = "MST",
                            day1 = "survey",
                            unmarkedMultFrameInput = TRUE)

ys.deeref <- ys.deerdh$effort
ys.deerdh <- ys.deerdh$detection_history


ys.Forest <- as.data.frame(substr(rownames(ys.deerdh),5,5))
ys.Fire <- as.data.frame(substr(rownames(ys.deerdh),7,7))
Years_PostFire <- as.data.frame(substr(rownames(ys.deerdh),11,11))

ys.covs <- cbind(ys.Forest, ys.Fire, Years_PostFire)
colnames(ys.covs) <- c("Forest", "Fire", "Years_PostFire")

ys.deerocc <- unmarkedFrameOccu(y = ys.deerdh, siteCovs = ys.covs)

summary(ys.deerocc)


# Null deer model with constant detection and constant occupancy
ys.d.1.1 <- occu(~1~1, data =  ys.deerocc)  #### detection first, then occupancy


ys.d.1.1.psi <- backTransform(ys.d.1.1, type = "state") #Occupancy


ys.d.1.1.p <- backTransform(ys.d.1.1, type = "det") #Detection


ys.d.1.1.psi.ci <- confint(ys.d.1.1.psi)
ys.d.1.1.p.ci <- confint(ys.d.1.1.p)

###Constant detection
ys.d.1.FoFiYf <- occu(~1 ~ Forest + Fire + Years_PostFire , data = ys.deerocc)


ys.d.1.FoFi <- occu(~1 ~ Forest + Fire , data = ys.deerocc)
ys.d.1.FoYf <- occu(~1 ~ Forest + Years_PostFire, data = ys.deerocc)
ys.d.1.FiYF <- occu(~1 ~ Fire + Years_PostFire, data = ys.deerocc)

ys.d.1.Yf <- occu(~1 ~ Years_PostFire, data = ys.deerocc)
ys.d.1.Fo <- occu(~1 ~ Forest, data = ys.deerocc)
ys.d.1.Fi <- occu(~1 ~ Fire, data = ys.deerocc)


#Constant occupancy
ys.d.FoFiYf.1 <- occu(~Forest + Fire + Years_PostFire ~1, data = ys.deerocc)

ys.d.FoFi.1 <- occu(~Forest + Fire ~1, data = ys.deerocc)
ys.d.FoYf.1 <- occu(~Forest + Years_PostFire ~1, data = ys.deerocc)
ys.d.FiYf.1 <- occu(~Fire + Years_PostFire ~1, data = ys.deerocc)

ys.d.Fo.1 <- occu(~ Forest ~1, data = ys.deerocc)
ys.d.Fi.1 <- occu(~ Fire ~1, data = ys.deerocc)
ys.d.Yf.1 <- occu(~ Years_PostFire ~1, data = ys.deerocc)

# Full model
ys.d.FoFiYf.FoFiYf <- occu(~Forest + Fire +Years_PostFire ~Forest+Fire + Years_PostFire, data = ys.deerocc)

ys.d.full.occ <- fitList(ys.d.1.1, ys.d.1.Fi, ys.d.1.FiYF, ys.d.1.Fo,
                         ys.d.1.FoFi, ys.d.1.FoFiYf, ys.d.1.FoYf, ys.d.Yf.1, ys.d.Fi.1, ys.d.Fo.1,
                         ys.d.FoFi.1, ys.d.FoFiYf.1, ys.d.FiYf.1, ys.d.FoYf.1, ys.d.FoFiYf.FoFiYf)

modSel(ys.d.full.occ)

ys.d.FoFiYf.1
pred.data <- expand.grid(Forest = levels(ys.deerocc@siteCovs$Forest), 
                       Fire = levels(ys.deerocc@siteCovs$Fire),
                       Years_PostFire = levels(ys.deerocc@siteCovs$Years_PostFire))

ys.full.mod.pred <- predict(ys.d.FoFiYf.1, type = "det", newdata = pred.data, append = TRUE)
ys.full.mod.pred

ggplot(data = ys.full.mod.pred, aes(Fire, Predicted, fill = Forest))+
  geom_boxplot()

y.full.dredge <- dredge(ys.d.FoFiYf.FoFiYf)

#### Model comparison

head(y.full.dredge)

# select models with the most support for model averaging (< 2 delta aicc)

ys.dredge.delta <- get.models(y.full.dredge, subset = delta <= 2)

ys.avg <- model.avg(ys.dredge.delta)

coef(ys.avg) %>%
  enframe


ys.avg.pred <- predict(ys.avg, type = "det", newdata = pred.data, append= TRUE)
ys.avg.pred 

ys.result <- cbind(pred.data, ys.avg.pred)

ggplot(data = ys.result, aes(Years_PostFire, fit))+
  geom_boxplot(fill = "grey")+
  theme_classic()

ggplot(data = ys.result, aes(Forest, fit))+
  geom_boxplot(fill = "grey")+
  theme_classic()

ggplot(data = ys.result, aes(Fire, fit))+
  geom_boxplot(fill = "grey")+
  theme_classic()

ggplot(data = ys.result, aes(Forest, fit, fill = Fire))+
  geom_boxplot()+
  theme_classic()

mean(ys.result[ys.result$Fire==0,4]) 
# mean Relative Habitat Use in unburned areas across all years and forest types: 0.32
mean(ys.result[ys.result$Fire==1,4]) 
# mean Relative Habitat Use in burned areas across all years and forest types: 0.37 ie 1.16 times greater than unburned
mean(ys.result[ys.result$Forest=="A",4]) 
# mean Relative Habitat Use in Aspen forests across all years and burn statuses: 0.27
mean(ys.result[ys.result$Forest=="M",4]) 
# mean Relative Habitat Use in Maple forests across all years and burn statuses: 0.33
mean(ys.result[ys.result$Forest=="J",4]) 
# mean Relative Habitat Use in Juniper forests across all years and burn statuses: 0.42 ie 1.56 times greater than aspen
mean(ys.result[ys.result$Years_PostFire==2,4]) 
# mean Relative Habitat Use in 2nd year postfire across forests and burn statuses: 0.45 ie 1.88 times greater than in the 3rd year
mean(ys.result[ys.result$Years_PostFire==3,4]) 
# mean Relative Habitat Use in 3rd year postfire across forests and burn statuses: 0.24
mean(ys.result[ys.result$Years_PostFire==4,4]) 
# mean Relative Habitat Use in 4th year postfire across forests and burn statuses: 0.35
mean(ys.result[ys.result$Years_PostFire==5,4]) 
# mean Relative Habitat Use in 5th year postfire across forests and burn statuses: 0.33

### Royle Nichols models

# Null deer model with constant detection and constant occupancy
ys.rn.1.1 <- occuRN(~1~1, data =  ys.deerocc)  #### detection first, then occupancy


ys.rn.1.1.psi <- backTransform(ys.rn.1.1, type = "state") #Occupancy


ys.rn.1.1.p <- backTransform(ys.rn.1.1, type = "det") #Detection


ys.rn.1.1.psi.ci <- confint(ys.rn.1.1.psi)
ys.rn.1.1.p.ci <- confint(ys.rn.1.1.p)

###Constant detection
ys.rn.1.FoFiYf <- occuRN(~1 ~ Forest + Fire + Years_PostFire , data = ys.deerocc)


ys.rn.1.FoFi <- occuRN(~1 ~ Forest + Fire , data = ys.deerocc)
ys.rn.1.FoYf <- occuRN(~1 ~ Forest + Years_PostFire, data = ys.deerocc)
ys.rn.1.FiYF <- occuRN(~1 ~ Fire + Years_PostFire, data = ys.deerocc)

ys.rn.1.Yf <- occuRN(~1 ~ Years_PostFire, data = ys.deerocc)
ys.rn.1.Fo <- occuRN(~1 ~ Forest, data = ys.deerocc)
ys.rn.1.Fi <- occuRN(~1 ~ Fire, data = ys.deerocc)


#Constant occupancy
ys.rn.FoFiYf.1 <- occuRN(~Forest + Fire + Years_PostFire ~1, data = ys.deerocc)

ys.rn.FoFi.1 <- occuRN(~Forest + Fire ~1, data = ys.deerocc)
ys.rn.FoYf.1 <- occuRN(~Forest + Years_PostFire ~1, data = ys.deerocc)
ys.rn.FiYf.1 <- occuRN(~Fire + Years_PostFire ~1, data = ys.deerocc)

ys.rn.Fo.1 <- occuRN(~ Forest ~1, data = ys.deerocc)
ys.rn.Fi.1 <- occuRN(~ Fire ~1, data = ys.deerocc)
ys.rn.Yf.1 <- occuRN(~ Years_PostFire ~1, data = ys.deerocc)

# Full model
ys.rn.FoFiYf.FoFiYf <- occuRN(~Forest + Fire +Years_PostFire ~Forest+Fire + Years_PostFire, data = ys.deerocc)

ys.rn.full.occ <- fitList(ys.rn.1.1, ys.rn.1.Fi, ys.rn.1.FiYF, ys.rn.1.Fo,
                  ys.rn.1.FoFi, ys.rn.1.FoFiYf, ys.rn.1.FoYf, ys.rn.Yf.1, ys.rn.Fi.1, ys.rn.Fo.1,
                  ys.rn.FoFi.1, ys.rn.FoFiYf.1, ys.rn.FiYf.1, ys.rn.FoYf.1, ys.rn.FoFiYf.FoFiYf)

modSel(ys.rn.full.occ)

ys.rn.1.FoFiYf


pred.data <- expand.grid(Forest = levels(ys.deerocc@siteCovs$Forest), 
                       Fire = levels(ys.deerocc@siteCovs$Fire),
                       Years_PostFire = levels(ys.deerocc@siteCovs$Years_PostFire))

ys.rn.full.mod.pred <- predict(ys.rn.FoFiYf.1, type = "det", newdata = pred.data, append = TRUE)
ys.rn.full.mod.pred

ggplot(data = ys.rn.full.mod.pred, aes(Years_PostFire, Predicted, fill = Fire))+
  geom_boxplot()

y.rn.full.dredge <- dredge(ys.rn.FoFiYf.FoFiYf)

#### Model comparison

head(y.rn.full.dredge)

# select models with the most support for model averaging (< 2 delta aicc)

ys.rn.dredge.delta <- get.models(y.rn.full.dredge, subset = delta <= 2)

ys.rn.avg <- model.avg(ys.dredge.delta)

coef(ys.rn.avg) %>%
  enframe

ys.rn.avg.pred <- predict(ys.rn.avg, type = "det", newdata = pred.data, append= TRUE)

ys.rn.result <- cbind(pred.data, ys.rn.avg.pred)
ys.rn.result

ggplot(data = ys.rn.result, aes(Years_PostFire, fit))+
  geom_boxplot(fill = "grey")+
  theme_classic()

ggplot(data = ys.rn.result, aes(Forest, fit))+
  geom_boxplot(fill = "grey")+
  theme_classic()

ggplot(data = ys.rn.result, aes(Fire, fit))+
  geom_boxplot(fill = "grey")+
  theme_classic()

ggplot(data = ys.rn.result, aes(Forest, fit, fill = Fire))+
  geom_boxplot()+
  theme_classic()

str(ys.rn.result)

mean(ys.rn.result[ys.rn.result$Fire==0,4]) 
# mean Relative Habitat Use in unburned areas across all years and forest types: 0.32
mean(ys.rn.result[ys.rn.result$Fire==1,4]) 
# mean Relative Habitat Use in burned areas across all years and forest types: 0.37 ie 1.16 times greater than unburned
mean(ys.rn.result[ys.rn.result$Forest=="A",4]) 
# mean Relative Habitat Use in Aspen forests across all years and burn statuses: 0.27
mean(ys.rn.result[ys.rn.result$Forest=="M",4]) 
# mean Relative Habitat Use in Maple forests across all years and burn statuses: 0.33
mean(ys.rn.result[ys.rn.result$Forest=="J",4]) 
# mean Relative Habitat Use in Juniper forests across all years and burn statuses: 0.42 ie 1.56 times greater than aspen
mean(ys.rn.result[ys.rn.result$Years_PostFire==2,4]) 
# mean Relative Habitat Use in 2nd year postfire across forests and burn statuses: 0.45 ie 1.88 times greater than in the 3rd year
mean(ys.rn.result[ys.rn.result$Years_PostFire==3,4]) 
# mean Relative Habitat Use in 3rd year postfire across forests and burn statuses: 0.24
mean(ys.rn.result[ys.rn.result$Years_PostFire==4,4]) 
# mean Relative Habitat Use in 4th year postfire across forests and burn statuses: 0.35
mean(ys.rn.result[ys.rn.result$Years_PostFire==5,4]) 
# mean Relative Habitat Use in 5th year postfire across forests and burn statuses: 0.33

```

Create a model selection table that includes coefficients

```{r}

occ.mod.sel <- as.data.frame(y.full.dredge)
test <- coef(y.full.dredge[1])
test[4]

coef(y.full.dredge)
occ.mod.sel <- cbind(y.full.dredge,coef(y.full.dredge))

head(occ.mod.sel)
getwd()
#write.csv(occ.mod.sel,"occ.mod.sel.csv")

```




If I understand this right I can show both the individual models for eahc of my covariates to demonstrate their effects,
and still show my model selection to show the most appropriate model. So, what I am going to do here is create constant
detection models for each covariate for occupancy and relative habitat use.

Occupancy
Fire
```{r}

ys.d.1.Fi <- occu(~1 ~ Fire, data = ys.deerocc)
pred.rep <- data.frame(Fire = c(0,1))
pred.rep$Fire <- as.factor(pred.rep$Fire)

occ.fi.pred <- predict(ys.d.1.Fi, type = "state", newdata = pred.rep, append = TRUE)
occ.fi.pred

occ.fi.pred |> ggplot(aes(Fire, Predicted))+
  geom_col(fill = "grey") + geom_errorbar(aes(x=Fire, ymin = lower,
                                ymax = upper), width = 0.2) + 
  theme_classic()


0.78/0.63
# times greater occupancy in burned than unburned areas

```

Forest
```{r}

ys.d.1.Fo <- occu(~1 ~ Forest, data = ys.deerocc)
pred.rep <- data.frame(Forest = c("A", "J", "M"))
pred.rep$Forest <- as.factor(pred.rep$Forest)

occ.fo.pred <- predict(ys.d.1.Fo, type = "state", newdata = pred.rep, append = TRUE)
occ.fo.pred

occ.fo.pred |> ggplot(aes(Forest, Predicted))+
  geom_col(fill = "grey") + geom_errorbar(aes(x=Forest, ymin = lower,
                                ymax = upper), width = 0.2) + 
  theme_classic()

```

Years post fire
```{r}

ys.d.1.Yf <- occu(~1 ~ Years_PostFire, data = ys.deerocc)
pred.rep <- data.frame(Years_PostFire = c(2,3,4,5))
pred.rep$Years_PostFire <- as.factor(pred.rep$Years_PostFire)

occ.Yf.pred <- predict(ys.d.1.Yf, type = "state", newdata = pred.rep, append = TRUE)
occ.Yf.pred

occ.Yf.pred |> ggplot(aes(Years_PostFire, Predicted))+
  geom_col(fill = "grey") + geom_errorbar(aes(x=Years_PostFire, ymin = lower,
                                ymax = upper), width = 0.2) + 
  theme_classic()

```

Relative Habitat Use
Fire

```{r}

ys.rn.1.Fi <- occuRN(~1 ~ Fire, data = ys.deerocc)
pred.rep <- data.frame(Fire = c(0,1))
pred.rep$Fire <- as.factor(pred.rep$Fire)

rn.fi.pred <- predict(ys.rn.1.Fi, type = "state", newdata = pred.rep, append = TRUE)
rn.fi.pred

rn.fi.pred |> ggplot(aes(Fire, Predicted))+
  geom_col(fill = "grey") + geom_errorbar(aes(x=Fire, ymin = lower,
                                ymax = upper), width = 0.2) + 
  theme_classic()

```

Forest

```{r}

ys.rn.1.Fo <- occuRN(~1 ~ Forest, data = ys.deerocc)
pred.rep <- data.frame(Forest = c("A", "J", "M"))
pred.rep$Forest <- as.factor(pred.rep$Forest)

rn.fo.pred <- predict(ys.rn.1.Fo, type = "state", newdata = pred.rep, append = TRUE)
rn.fo.pred

rn.fo.pred |> ggplot(aes(Forest, Predicted))+
  geom_col(fill = "grey") + geom_errorbar(aes(x=Forest, ymin = lower,
                                ymax = upper), width = 0.2) + 
  theme_classic()

```

Years Postfire

```{r}

ys.rn.1.Yf <- occuRN(~1 ~ Years_PostFire, data = ys.deerocc)
pred.rep <- data.frame(Years_PostFire = c(2,3,4,5))
pred.rep$Years_PostFire <- as.factor(pred.rep$Years_PostFire)

rn.Yf.pred <- predict(ys.rn.1.Yf, type = "state", newdata = pred.rep, append = TRUE)
rn.Yf.pred

rn.Yf.pred |> ggplot(aes(Years_PostFire, Predicted))+
  geom_col(fill = "grey") + geom_errorbar(aes(x=Years_PostFire, ymin = lower,
                                ymax = upper), width = 0.2) + 
  theme_classic()

```




